---
title: "Descriptive Statistiscs & Data Processing"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### Packages
```{r include=FALSE}

require(dplyr)  
require(tidyr)  
require(stringr)
require(tibble) 
require(zipcodeR)
require(janitor)
require(writexl)
require(ggplot2)
require(rlang)
require(knitr)  
```

### Data Import
```{r, echo= TRUE}
# ---- Set Paths ----
base     <- normalizePath(file.path("..", ".."), mustWork = FALSE)
analyses <- file.path(base, "analyses")
inp      <- file.path(analyses, "inputs")

# ---- Load Raw Datasets ----
surv <- read.csv(file.path(inp, "progover60.csv"))   # Main Qualtrics dataset
prog <- read.csv(file.path(inp, "prog.csv"))         # Optional secondary file

# ---- Bin Completion Scores ----
intFUN <- function(df, column = "PROG") {
  df %>%
    mutate(
      prog_bin = cut(
        .data[[column]],
        breaks = seq(0, 100, by = 10),
        include.lowest = TRUE,
        right = FALSE,
        labels = paste0(seq(0, 90, 10), "-", seq(10, 100, 10), "%")
      )
    ) %>%
    count(prog_bin, name = "Respondent_Count") %>%
    arrange(prog_bin)
}

TPROG <- intFUN(prog)
PROG  <- intFUN(surv)


```
## Functions
```{r, echo= TRUE}
#| echo: true

#----------- Basic Summary Stats for Continuous/Categorical -----------------

sumFUN <- function(df) {
  summary_list <- list()
  
  for (colname in names(df)) {
    column <- df[[colname]]
    
    if (is.numeric(column)) {
 # Continuous variable summary
      summary_list[[colname]] <- tibble::tibble(
        Variable = colname,
        Type = "Continuous",
        N = sum(!is.na(column)),
        Mean = mean(column, na.rm = TRUE),
        Median = median(column, na.rm = TRUE),
        SD = sd(column, na.rm = TRUE),
        Min = min(column, na.rm = TRUE),
        Max = max(column, na.rm = TRUE)
      )
    } else if (is.factor(column) || is.character(column) || is.logical(column)) {
 # Categorical variable summary
      freq_table <- as.data.frame(table(column, useNA = "ifany"))
      names(freq_table) <- c("Level", "Count")
      freq_table$Variable <- colname
      freq_table$Proportion <- freq_table$Count / sum(freq_table$Count)
      freq_table <- freq_table[, c("Variable", "Level", "Count", "Proportion")]
      summary_list[[colname]] <- freq_table
    }
  }
  return(summary_list)
}

#----------------- Response Count (for numeric columns) -------------------
uniFUN <- function(df, columns = NULL) {
  if (is.null(columns)) {
    columns <- names(df)
  }
  list <- list()
  for (col in columns) {
    if (col %in% names(df)) {
      list[[col]] <- df %>%
        count(!!sym(col), name = "Count") %>%
        arrange(desc(Count))
    } else {
      warning(paste("Column", col, "not found in data."))
    }
  }
  return(list)
}

#-------------- Cronbach's alpha -------------
compute_alpha <- function(df, vars, label = "Scale") {
  input_data <- df %>%
    select(all_of(vars)) %>%
    drop_na() %>%
    as.data.frame()
  
  alpha_result <- psych::alpha(input_data)
  
  cat(paste0("\n🔹 Cronbach's Alpha for ", label, ":\n"))
  print(round(alpha_result$total$raw_alpha, 3))
  return(alpha_result)
}

```

# QUALTRICS METADATA
#### Data Manipulation
```{r, echo = TRUE}

# ---- Filter out partial or rushed responses ----
surv <- surv %>%
  filter(PROG >= 70) %>%                        # 70%+ completion
  mutate(DURATIONmin = DURATION / 60) %>%       # Convert seconds to minutes
  filter(DURATIONmin >= 5)                      # At least 5 minutes spent


# ---- Optional: Duration intervals for visual summaries ----
MD <- surv %>%
  filter(DURATIONmin < 45)  # Remove outliers

max_min <- ceiling(max(MD$DURATIONmin, na.rm = TRUE) / 10) * 10
breaks <- seq(0, max_min, by = 5)
labels <- paste0(head(breaks, -1), "-", tail(breaks, -1), " min")

MD <- MD %>%
  mutate(DURATIONminint = cut(
    DURATIONmin,
    breaks = breaks,
    include.lowest = TRUE,
    right = FALSE,
    labels = labels
  ))

```


#### Descriptive Statistics 
```{r, echo = TRUE}

# ---- Descriptive stats of metadata fields ----
survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# Selected summaries
survsum$PROG
survsum$DURATIONmin
survsum$FINISHED
survsum$QSCORE
survsum$RECDATE

# Frequency tables
table(surv$PROG)
table(surv$DURATIONmin)
table(surv$FINISHED)


```



# DEMOGRAPHICS
#### Data Manipulation
```{r, echo = TRUE}
# ---- Calculate Age from Year of Birth ----
surv <- surv %>%
  mutate(
    AGE = 2024 - DOB,
    AGEint = cut(
      AGE,
      breaks = c(0, 29, 39, 49, 59, Inf),
      labels = c("20–29", "30–39", "40–49", "50–59", "60+"),
      right = TRUE,
      include.lowest = TRUE
    )
  )

# ---- Add County from ZIP ----
zip_info <- zipcodeR::zip_code_db %>%
  select(zipcode, county, state)

surv <- surv %>%
  mutate(ZIPCODE = as.character(ZIPCODE)) %>%
  left_join(zip_info, by = c("ZIPCODE" = "zipcode")) %>%
  rename(LOCATION = county) %>%
  select(-state)

```

#### Descriptive Statistics
```{r, echo = TRUE}

# Run summaries
survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# Key demographics
survsum$AGE
survsum$AGEint
survsum$RACE
survsum$ETHNICITY
survsum$GENDER
survsum$INCOME
survsum$EDUCATION
survsum$DEGREE
survsum$TWS
survsum$COURSE
survsum$COURSETIME
survsum$SELFTITLE
survsum$AFFILIATE
survsum$BIOTIME
survsum$ACTIVITY
survsum$LICENSE

# Optional free-text or categorical (if filled)
survsum$othACTIVITY
survsum$othAFFILIATE


```
#### Variable Processing
```{r, echo = TRUE}
# Compute median for age binning
age_median <- median(surv$AGE, na.rm = TRUE)

# Binary transformations
surv <- surv %>%
  mutate(
    AGEbin = if_else(AGE <= age_median, 0L, 1L),
    RACEbin = case_when(
      RACE == "White" ~ 1L,
      RACE %in% c("Asian", "Black or African American", "Other") ~ 0L,
      RACE == "I prefer not to answer" ~ NA_integer_,
      TRUE ~ NA_integer_
    ),
    GENDERbin = case_when(
      GENDER == "Male" ~ 1L,
      GENDER == "Female" ~ 0L,
      GENDER %in% c("Other", "I prefer not to answer") ~ NA_integer_,
      TRUE ~ NA_integer_
    ),
    INCOMEbin = if_else(INCOME > 62027, 1L, 0L),
    EDUCATIONbin = case_when(
      EDUCATION %in% c("College Graduate/BA or BS (4-year degree)", "Graduate or Professional School") ~ 1L,
      EDUCATION %in% c("Did not graduate high school/no GED", "High school graduate/GED",
                       "Technical/Vocational School", "Some College/AA or AS (2-year degree)") ~ 0L,
      TRUE ~ NA_integer_
    ),
    DEGREEbin     = if_else(DEGREE == "Yes", 1L, if_else(DEGREE == "No", 0L, NA_integer_)),
    TWSbin        = if_else(TWS == "Yes", 1L, if_else(TWS == "No", 0L, NA_integer_)),
    COURSEbin     = if_else(COURSE == "Yes", 1L, if_else(COURSE == "No", 0L, NA_integer_)),
    SELFTITLEbin  = if_else(SELFTITLE == "Yes", 1L, if_else(SELFTITLE == "No", 0L, NA_integer_)),
    LICENSEbin    = if_else(LICENSE == "Yes", 1L, if_else(LICENSE == "No", 0L, NA_integer_)),
    COURSETIMEbin = case_when(
      COURSETIME %in% c("<5 years", "5-10 years") ~ 1L,
      COURSETIME == ">10 years" ~ 0L,
      TRUE ~ NA_integer_
    ),
    BIOTIMEbin = case_when(
      BIOTIME %in% c("10-20 years", ">20 years") ~ 1L,
      BIOTIME %in% c("<1 year", "1-5 years", "5-10 years") ~ 0L,
      TRUE ~ NA_integer_
    )
  )

# Frequency tables
table(surv$AGEbin)
table(surv$AGEint)
table(surv$RACEbin)
table(surv$GENDERbin)
table(surv$INCOMEbin)
table(surv$EDUCATIONbin)
table(surv$DEGREEbin)
table(surv$TWSbin)
table(surv$COURSEbin)
table(surv$COURSETIMEbin)
table(surv$SELFTITLEbin)
table(surv$LICENSEbin)
table(surv$BIOTIMEbin)

```


# KNOWLEDGE

#### Data Manipulation
```{r, echo = TRUE}

# Define correct answers
answers <- list(
  PIGS       = "True",       
  BRUCE      = "False",      
  CWD        = "False",      
  FLUAL      = "True",       
  FLU        = "False",      
  COVID      = "True",       
  COVIDSPILL = "False",      
  RABIESAL   = "False",      
  RABIES     = "Bites",      
  TURKEY     = "Incinerate"
)

# Scoring knowledge items
surv <- surv %>%
  mutate(across(all_of(names(answers)), ~ tolower(str_trim(as.character(.))))) %>%
  rowwise() %>%
  mutate(
    across(all_of(names(answers)),
           list(
             corr = ~ as.integer(. == tolower(answers[[cur_column()]])),
             cert = ~ as.integer(. != "i don't know" & !is.na(.))
           ),
           .names = "{.col}{.fn}"),
    CORRECTnum  = sum(c_across(ends_with("corr")), na.rm = TRUE),
    CERTAINnum  = sum(c_across(ends_with("cert")), na.rm = TRUE)
  ) %>%
  ungroup()

```

#### Descriptive Statistics
```{r, echo = TRUE}
# Generate summaries
survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# Individual question responses
survsum$PIGS; survsum$BRUCE; survsum$CWD; survsum$FLUAL
survsum$COVID; survsum$COVIDSPILL; survsum$RABIESAL; survsum$RABIES; survsum$TURKEY

# Correctness per question
survsum$PIGScorr; survsum$BRUCEcorr; survsum$CWDcorr
survsum$FLUALcorr; survsum$COVIDcorr; survsum$COVIDSPILLcorr
survsum$RABIESALcorr; survsum$RABIEScorr; survsum$TURKEYcorr

# Certainty per question
survsum$PIGScert; survsum$BRUCEcert; survsum$CWDcert
survsum$FLUALcert; survsum$COVIDcert; survsum$COVIDSPILLcert
survsum$RABIEScert; survsum$RABIESALcert; survsum$TURKEYcert

# Composite scores
survsum$CORRECTnum
survsum$CERTAINnum

```

#### Variable Processing
```{r, echo = TRUE}

# Compute cutoffs
CORRECTmed  <- median(surv$CORRECTnum, na.rm = TRUE)
CORRECTavg  <- mean(surv$CORRECTnum, na.rm = TRUE)
CERTAINmed  <- median(surv$CERTAINnum, na.rm = TRUE)
CERTAINavg  <- mean(surv$CERTAINnum, na.rm = TRUE)

# Binary splits
surv <- surv %>%
  mutate(
    CORRECTmed  = if_else(CORRECTnum > CORRECTmed, 1L, 0L),
    CORRECTavg  = if_else(CORRECTnum > CORRECTavg, 1L, 0L),
    CERTAINmed  = if_else(CERTAINnum > CERTAINmed, 1L, 0L),
    CERTAINavg  = if_else(CERTAINnum > CERTAINavg, 1L, 0L)
  )

# Tabulations
table(surv$CORRECTnum)
table(surv$CERTAINnum)
table(surv$CORRECTmed)
table(surv$CORRECTavg)
table(surv$CERTAINmed)
table(surv$CERTAINavg)

# Print thresholds
CORRECTmed; CORRECTavg
CERTAINmed; CERTAINavg


```


# ATTITUDES
#### Data Manipulation
```{r, echo = TRUE}

# Define attitude items
attitude_forward <- c("CWDAL", "BATS", "PPEREQ", "EHD", "POPPLAN", "SURVEY",
                      "VACCINE", "PREVAL", "DIVERSE", "CONSEQ", "CLIMATE", "EDREQ", "INFO")
attitude_reverse <- c("DARWIN", "POPRED", "HANDSON")
attitude_all <- c(attitude_forward, attitude_reverse)

# Recode 5-point Likert to 3 levels
surv <- surv %>%
  mutate(across(all_of(attitude_forward),
                ~ case_when(
                  . %in% c("Strongly Agree", "Agree")            ~ "Favorable",
                  . == "Neutral"                                 ~ "Neutral",
                  . %in% c("Disagree", "Strongly Disagree")      ~ "Unfavorable",
                  TRUE                                           ~ NA_character_),
                .names = "{.col}att")) %>%
  mutate(across(all_of(attitude_reverse),
                ~ case_when(
                  . %in% c("Strongly Disagree", "Disagree")      ~ "Favorable",
                  . == "Neutral"                                 ~ "Neutral",
                  . %in% c("Agree", "Strongly Agree")            ~ "Unfavorable",
                  TRUE                                           ~ NA_character_),
                .names = "{.col}att"))

# Convert to ordered factor for consistency
surv <- surv %>%
  mutate(across(ends_with("att"),
                ~ factor(.x, levels = c("Unfavorable", "Neutral", "Favorable"), ordered = TRUE)))


```

#### Descriptive Statistics
```{r, echo = TRUE}
# Summary tables for original and recoded
survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# 5-point raw responses
lapply(attitude_all, function(v) survsum[[v]])

# 3-point recoded
attitude_att_vars <- paste0(attitude_all, "att")
lapply(attitude_att_vars, function(v) survsum[[v]])


```
#### Variable Processing
```{r, echo = TRUE}

# Convert recoded attitudes to numeric: 0 = Unfavorable, 1 = Neutral, 2 = Favorable
surv <- surv %>%
  mutate(across(all_of(attitude_att_vars),
                ~ recode(.x,
                         "Unfavorable" = 0L,
                         "Neutral"     = 1L,
                         "Favorable"   = 2L),
                .names = "{.col}num"))

attitude_num_vars <- paste0(attitude_att_vars, "num")

# Composite score
surv <- surv %>%
  mutate(ATTITUDEnum = rowSums(across(all_of(attitude_num_vars)), na.rm = TRUE))

# Median cutoff
attitude_median <- median(surv$ATTITUDEnum, na.rm = TRUE)

# Binary split: above median = 1
surv <- surv %>%
  mutate(ATTITUDEbin = if_else(ATTITUDEnum > attitude_median, 1L, 0L))

# Count responses by type
surv <- surv %>%
  rowwise() %>%
  mutate(
    FAVnum     = sum(c_across(all_of(attitude_att_vars)) == "Favorable", na.rm = TRUE),
    NEUTRALnum = sum(c_across(all_of(attitude_att_vars)) == "Neutral", na.rm = TRUE),
    UNFAVnum   = sum(c_across(all_of(attitude_att_vars)) == "Unfavorable", na.rm = TRUE)
  ) %>%
  ungroup()

# Median thresholds
fav_median     <- median(surv$FAVnum, na.rm = TRUE)
neutral_median <- median(surv$NEUTRALnum, na.rm = TRUE)
unfav_median   <- median(surv$UNFAVnum, na.rm = TRUE)

# Binary splits
surv <- surv %>%
  mutate(
    FAVbin     = if_else(FAVnum     > fav_median,     1L, 0L),
    NEUTRALbin = if_else(NEUTRALnum > neutral_median, 1L, 0L),
    UNFAVbin   = if_else(UNFAVnum   > unfav_median,   1L, 0L)
  )

# Composite and binary summaries
table(surv$ATTITUDEnum)
table(surv$ATTITUDEbin)

# Breakdown counts
table(surv$FAVnum)
table(surv$FAVbin)
table(surv$NEUTRALnum)
table(surv$NEUTRALbin)
table(surv$UNFAVnum)
table(surv$UNFAVbin)

# Print thresholds
attitude_median
fav_median
neutral_median
unfav_median


```

# PRACTICES
#### Data Manipulation
```{r, echo = TRUE}

# Count the number of counties listed (multi-select checkbox)
surv <- surv %>%
  mutate(nCOUNTIES = if_else(is.na(COUNTIES), NA_integer_, str_count(COUNTIES, ",") + 1L))

```

#### Descriptive Statistics
```{r, echo = TRUE}

survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# Core field practice items
survsum$CONTACT
survsum$FIELD
survsum$COLLECT
survsum$HANDLE
survsum$STATE
survsum$PPE
survsum$PPETIME
survsum$COUNTIES
survsum$nCOUNTIES


```

#### Variable Processing
```{r, echo= TRUE}

# Create binary versions of key behaviors
surv <- surv %>%
  mutate(
    nCOUNTIESbin = if_else(is.na(nCOUNTIES), NA_integer_, nCOUNTIES),
    COLLECTbin   = if_else(COLLECT == "Yes", 1L, if_else(COLLECT == "No", 0L, NA_integer_)),
    HANDLEbin    = if_else(HANDLE == "Yes", 1L, if_else(HANDLE == "No", 0L, NA_integer_)),
    PPEbin       = if_else(PPE == "No", 1L, if_else(PPE == "Yes", 0L, NA_integer_)),  # Risk if not using PPE
    FIELDbin     = if_else(FIELD >= 50, 1L, 0L),  # ≥50% time in field
    STATEbin     = case_when(
      STATE == "Dead" ~ 0L,
      STATE %in% c("Alive - Sedated", "Alive - Not Sedated") ~ 1L,
      TRUE ~ NA_integer_
    ),
    CONTACTbin = case_when(
      CONTACT %in% c("Daily", "Weekly", "Monthly") ~ 1L,
      CONTACT %in% c("Rarely", "Never") ~ 0L,
      TRUE ~ NA_integer_
    )
  )

# Compute binary summary and risk score
counties_median <- median(surv$nCOUNTIES, na.rm = TRUE)

surv <- surv %>%
  mutate(
    COUNTIESbin = if_else(nCOUNTIES > counties_median, 1L, 0L),
    PRACnum = rowSums(across(c(CONTACTbin, FIELDbin, COLLECTbin, HANDLEbin, COUNTIESbin, PPEbin)), na.rm = TRUE)
  )

# Median threshold and binary split
prac_median <- median(surv$PRACnum, na.rm = TRUE)
surv <- surv %>%
  mutate(PRACbin = if_else(PRACnum >= prac_median, 1L, 0L))

# Individual binary variable checks
table(surv$CONTACTbin)
table(surv$FIELDbin)
table(surv$COLLECTbin)
table(surv$HANDLEbin)
table(surv$PPEbin)
table(surv$STATEbin)
table(surv$COUNTIESbin)

# Composite scores
table(surv$PRACnum)
table(surv$PRACbin)

# Medians
counties_median
prac_median


```

# INTEREST
#### Data Manipulation
```{r, echo = TRUE}

# Count options selected in multi-select fields
surv <- surv %>%
  mutate(
    nFREEINFO = if_else(is.na(FREEINFO), NA_integer_, str_count(FREEINFO, ",") + 1L),
    nTOPICS   = if_else(is.na(TOPICS),   NA_integer_, str_count(TOPICS, ",") + 1L),
    nSOURCE   = if_else(is.na(SOURCE),   NA_integer_, str_count(SOURCE, ",") + 1L))


```
#### Descriptive Statistics
```{r, echo = TRUE}

survsum <- sumFUN(surv)
survuni <- uniFUN(surv)

# Raw interest fields
survsum$ACCESS
survsum$INTEREST
survsum$FREEINFO
survsum$SOURCE
survsum$TOPICS

# Option counts
survsum$nFREEINFO
survsum$nTOPICS
survsum$nSOURCE

```
#### Variable Processing
```{r, echo= TRUE}
# Recode 3-level interest items: EDREQ, INFO (forward), HANDSON (reverse)
edu_forward <- c("EDREQ", "INFO")
edu_reverse <- c("HANDSON")

# Convert Likert to 'More', 'Neutral', 'Less'
surv <- surv %>%
  mutate(across(all_of(c(edu_forward, edu_reverse)), as.character)) %>%
  mutate(across(all_of(edu_forward),
                ~ case_when(
                    . %in% c("Strongly Agree", "Agree")       ~ "More",
                    . == "Neutral"                            ~ "Neutral",
                    . %in% c("Disagree", "Strongly Disagree") ~ "Less",
                    TRUE                                      ~ NA_character_),
                .names = "{.col}edu")) %>%
  mutate(across(all_of(edu_reverse),
                ~ case_when(
                    . %in% c("Strongly Disagree", "Disagree") ~ "More",
                    . == "Neutral"                            ~ "Neutral",
                    . %in% c("Agree", "Strongly Agree")       ~ "Less",
                    TRUE                                      ~ NA_character_),
                .names = "{.col}edu")) %>%
  mutate(across(ends_with("edu"), ~ factor(.x, levels = c("More", "Neutral", "Less"), ordered = TRUE)))

# Forward: More = 2, Neutral = 1, Less = 0
surv <- surv %>%
  mutate(across(all_of(c("EDREQedu", "HANDSONedu")),
                ~ recode(.x, "More" = 2L, "Neutral" = 1L, "Less" = 0L),
                .names = "{.col}num"))

# Reverse: INFOedu — More = 0, Neutral = 1, Less = 2
surv <- surv %>%
  mutate(INFOedunum = recode(INFOedu, "More" = 0L, "Neutral" = 1L, "Less" = 2L))

# Binary indicators for info-seeking behavior
freeinfo_median <- median(surv$nFREEINFO, na.rm = TRUE)
topics_median   <- median(surv$nTOPICS, na.rm = TRUE)
source_median   <- median(surv$nSOURCE, na.rm = TRUE)

surv <- surv %>%
  mutate(
    FREEINFOedu = if_else(nFREEINFO >= freeinfo_median, 1L, 0L),
    TOPICSedu   = if_else(nTOPICS   >= topics_median,   1L, 0L),
    SOURCEedu   = if_else(nSOURCE   >= source_median,   1L, 0L),
    ACCESSedu   = case_when(
      ACCESS == "Yes" ~ 1L,
      ACCESS == "No"  ~ 0L,
      TRUE ~ NA_integer_
    ),
    INTERESTedu = case_when(
      INTEREST == "Yes"    ~ 2L,
      INTEREST == "Unsure" ~ 1L,
      INTEREST == "No"     ~ 0L,
      TRUE                 ~ NA_integer_
    )
  )

# Compute composite score
interest_components <- c(
  "FREEINFOedu", "TOPICSedu", "SOURCEedu", "ACCESSedu", "INTERESTedu",
  "HANDSONedunum", "INFOedunum", "EDREQedunum"
)

surv <- surv %>%
  mutate(INFOnum = rowSums(across(all_of(interest_components)), na.rm = TRUE))

# Binary split
info_median <- median(surv$INFOnum, na.rm = TRUE)
surv <- surv %>%
  mutate(INFObin = if_else(INFOnum > info_median, 1L, 0L))

# Individual components
table(surv$nFREEINFO)
table(surv$nTOPICS)
table(surv$nSOURCE)
table(surv$FREEINFOedu)
table(surv$TOPICSedu)
table(surv$SOURCEedu)
table(surv$ACCESSedu)
table(surv$INTERESTedu)

# Composite interest
table(surv$INFOnum)
table(surv$INFObin)

# Thresholds
freeinfo_median
topics_median
source_median
info_median

```

## Cronbach's Alpha Calculations
```{r, echo= TRUE}

require(psych)
#---------------------- KNOWLEDGE ----------------------
knowledge_vars <- c("PIGScorr", "BRUCEcorr", "CWDcorr", "FLUALcorr",
                    "COVIDcorr", "COVIDSPILLcorr", "RABIESALcorr", 
                    "RABIEScorr", "TURKEYcorr")

knowledge_alpha <- compute_alpha(surv, knowledge_vars, "Knowledge")

#---------------------- ATTITUDES ----------------------
attitude_vars <- c("CWDALattnum", "BATSattnum", "PPEREQattnum", "EHDattnum",
                   "POPPLANattnum", "SURVEYattnum", "VACCINEattnum",
                   "PREVALattnum", "DIVERSEattnum", "CONSEQattnum",
                   "CLIMATEattnum", "EDREQattnum", "INFOattnum",
                   "DARWINattnum", "POPREDattnum", "HANDSONattnum")

attitude_alpha <- compute_alpha(surv, attitude_vars, "Attitudes")

#---------------------- PRACTICES ----------------------
practice_vars <- c("CONTACTbin", "FIELDbin", "COLLECTbin", "HANDLEbin",
                   "COUNTIESbin", "PPEbin")

practice_alpha <- compute_alpha(surv, practice_vars, "Practices")

#---------------------- INTEREST ----------------------
interest_vars <- c("FREEINFOedu", "TOPICSedu", "SOURCEedu", "ACCESSedu", "INTERESTedu",
                   "HANDSONedunum", "INFOedunum", "EDREQedunum")

interest_alpha <- compute_alpha(surv, interest_vars, "Interest")


```


# EXPORTS
### Data Frames
```{r}
#| include: false

###### Processed Responses ######
oup = file.path(analyses, "outputs")
write.csv(surv, file.path(oup, "processedsurv.csv"), row.names = FALSE)

```



# References
```{r}
# 
# RStudio.Version() 
# version$version.string
# citation()
# 
# #### to display the packages within the .qmd without creating another .bib ####
# knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='')
# 
```

