---
title: "Chi-Squared Analysis of Binary Variables"
date: "`r Sys.Date()`"
format: 
  html:
    html-table-processing: none
    toc: true
    toc-depth: 4
    toc-location: left
    number-sections: true
    code-fold: true
    code-summary: "Show Code"
    fig-cap-location: bottom
    smooth-scroll: true
    theme: flatly
    font-family: serif
    font-size: 12px
    line-height: 150%
    css: styles.css  # Reference your CSS file here
editor: 
  markdown: 
    wrap: 72
---

# Initialization

```{r include=FALSE}

require(rcompanion)

base = normalizePath(file.path("..", ".."), mustWork = FALSE)  
analyses = file.path(base, "analyses")
oup = file.path(analyses, "outputs")

surv = read.csv(file.path(oup, "binaryCombined.csv"))
surv 

```

# Function
```{r}

cramerschi<-function(a,b){
   
   data.table <- table(a,b) 
   data.chi <- chisq.test(data.table)
   col_counts <- colSums(data.table)
   data.table_with_counts <- rbind(data.table, Col_Counts = col_counts)
   CramV<-as.numeric(cramerV(data.table))
  #assign outputs
    chistat<-as.numeric(data.chi$statistic)
   chi.df<-as.integer(data.chi$parameter)
   chi.pvalue<-data.chi$p.value
   zero_zero<-data.table_with_counts[1,1]
   zero_one<-data.table_with_counts[2,1]
   one_zero<-data.table_with_counts[1,2]
   one_one<-data.table_with_counts[2,2]
   colzerotot<-data.table_with_counts[3,1]
   colonetot<-data.table_with_counts[3,2]
   total.output<-c(chistat,chi.df, chi.pvalue, CramV, zero_zero, zero_one,
                           one_zero, one_one,colzerotot,colonetot)
  
   
   return(total.output)
 }
 
 
  #create vector of label for output string
cramerschi.output.list<-c("chistat","chi.df", "chi.pvalue", "CramV", "zero_zero", "zero_one",
                        "one_zero", "one_one","colzerotot","colonetot")


 #output will follow top row then first column of chiX table
 #X zeroone is the column "0" and the row "1"
 #columns will be second variable in comparison
 #rows will be first listed

```

# Manual comparison for output

This is just a visual of what the output would look like in a chi square table

```{r}
#Test comparison to compare to true ChiX table from degree x certain50
 
 
 
 data.table.test <- table(surv$AGE, surv$CORRECTmed)
 data.chi.test <- chisq.test(data.table.test)
 print(data.chi.test)
 col_counts.test <- colSums(data.table.test)
 col_counts.test
 data.table_with_counts.test <- rbind(data.table.test, Col_Counts = col_counts.test)
 print(data.table_with_counts.test)
 
 #compare this to
agexcorrmed<-cramerschi(surv$AGE, surv$CORRECTmed)
 data.frame(cramerschi.output.list,agexcorrmed)
```

# Demographic Information vs Knowledge and Certainty

```{r}
#in general we need to compare Demographic<->knowledge, Dem<->Certainty, Education<->{Knowledge,Certainty}
#Opinion<->{knowledge, certainty}, knowledge<->certainty
#the knowledge and certainty categories are summarized at the end to use in a 
#binary classification rather than put them all together
#maybe do handling and field work vs knowledge and cert
#handling and ppe

#Age
agexcorrmed<-cramerschi(surv$AGE, surv$CORRECTmed)
agexcorr50<-cramerschi(surv$AGE, surv$CORRECT50)
agexcertmed<-cramerschi(surv$AGE, surv$CERTAINmed)
agexcert50<-cramerschi(surv$AGE, surv$CERTAIN50)

#gender
genxcorrmed<-cramerschi(surv$GENDER, surv$CORRECTmed)
genxcorr50<-cramerschi(surv$GENDER, surv$CORRECT50)
genxcertmed<-cramerschi(surv$GENDER, surv$CERTAINmed)
genxcert50<-cramerschi(surv$GENDER, surv$CERTAIN50)

#income
incomexcorrmed<-cramerschi(surv$INCOME, surv$CORRECTmed)
incomexcorr50<-cramerschi(surv$INCOME, surv$CORRECT50)
incomexcertmed<- cramerschi(surv$INCOME, surv$CERTAINmed)
incomexcert50<-cramerschi(surv$INCOME, surv$CERTAIN50)


#age, gender, income
demoxknowcert<-data.frame(cramerschi.output.list, agexcert50, agexcertmed, agexcorr50, agexcorrmed,
 genxcert50, genxcertmed, genxcorr50, genxcorrmed,
 incomexcert50, incomexcertmed, incomexcorr50, incomexcorrmed
)

View(demoxknowcert)
```

# Education vs Knowledge and Certainty

```{r}
#degree
degreexcorrmed<-cramerschi(surv$DEGREE, surv$CORRECTmed)
degreexcorr50<-cramerschi(surv$DEGREE,surv$CORRECT50)
degreexcertmed<-cramerschi(surv$DEGREE, surv$CERTAINmed)
degreexcert50<-cramerschi(surv$DEGREE, surv$CERTAIN50)

#TWS
twsxcorrmed<-cramerschi(surv$TWS, surv$CORRECTmed)
twsxcorr50<- cramerschi(surv$TWS, surv$CORRECT50)
twsxcertmed<-cramerschi(surv$TWS, surv$CERTAINmed)
twsxcert50<-cramerschi(surv$TWS, surv$CERTAIN50)

#course
coursexcorrmed<-cramerschi(surv$COURSE, surv$CORRECTmed)
coursexcorr50<-cramerschi(surv$COURSE, surv$CORRECT50)
coursexcertmed<-cramerschi(surv$COURSE, surv$CERTAINmed)
coursexcert50<-cramerschi(surv$COURSE, surv$CERTAIN50)

#Selftitle
titlexcorrmed<-cramerschi(surv$SELFTITLE, surv$CORRECTmed)
titlexcorr50<-cramerschi(surv$SELFTITLE, surv$CORRECT50)
titlexcertmed<-cramerschi(surv$SELFTITLE, surv$CERTAINmed)
titlexcert50<-cramerschi(surv$SELFTITLE, surv$CERTAIN50)

#biotime
biotimexcorrmed<-cramerschi(surv$BIOTIME, surv$CORRECTmed)
biotimexcorr50<-cramerschi(surv$BIOTIME, surv$CORRECT50)
biotimexcertmed<-cramerschi(surv$BIOTIME, surv$CERTAINmed)
biotimexcert50<-cramerschi(surv$BIOTIME, surv$CERTAIN50)

#education
eduxcorrmed<-cramerschi(surv$EDUCATION, surv$CORRECTmed)
eduxcorr50<-cramerschi(surv$EDUCATION, surv$CORRECT50)
eduxcertmed<-cramerschi(surv$EDUCATION, surv$CERTAINmed)
eduxcert50<-cramerschi(surv$EDUCATION, surv$CERTAIN50)

#degree, tws, course, selftitle, biotime, education
eduxknowcert<-data.frame(cramerschi.output.list, 
      degreexcert50, degreexcertmed, degreexcorr50, degreexcorrmed,
      twsxcert50,twsxcertmed, twsxcorr50, twsxcorrmed,
      coursexcert50, coursexcertmed, coursexcorr50, coursexcorrmed,
      titlexcert50, titlexcertmed, titlexcorr50, titlexcorrmed,
      biotimexcert50, biotimexcertmed, biotimexcorr50, biotimexcorrmed,
      eduxcert50, eduxcertmed, eduxcorr50, eduxcorrmed
)
View(eduxknowcert)
```

# Field and Handling vs Knowledge and Certainty

```{r}
#contact
contactxcorrmed<-cramerschi(surv$CONTACT, surv$CORRECTmed)
contactxcorr50<-cramerschi(surv$CONTACT, surv$CORRECT50)
contactxcertmed<-cramerschi(surv$CONTACT, surv$CERTAINmed)
contactxcert50<-cramerschi(surv$CONTACT, surv$CERTAIN50)

#field
fieldxcorrmed<-cramerschi(surv$FIELD, surv$CORRECTmed)
fieldxcorr50<-cramerschi(surv$FIELD, surv$CORRECT50)
fieldxcertmed<-cramerschi(surv$FIELD, surv$CERTAINmed)
fieldxcert50<-cramerschi(surv$FIELD, surv$CERTAIN50)

#collect
collectxcorrmed<-cramerschi(surv$COLLECT, surv$CORRECTmed)
collectxcorr50<-cramerschi(surv$COLLECT, surv$CORRECT50)
collectxcertmed<-cramerschi(surv$COLLECT, surv$CERTAINmed)
collectxcert50<-cramerschi(surv$COLLECT, surv$CERTAIN50)

#handle
handlexcorrmed<-cramerschi(surv$HANDLE, surv$CORRECTmed)
handlexcorr50<-cramerschi(surv$HANDLE, surv$CORRECT50)
handlexcertmed<-cramerschi(surv$HANDLE, surv$CERTAINmed)
handlexcert50<-cramerschi(surv$HANDLE, surv$CERTAIN50)

#contact, field, collect, handle

fieldxknowcert<-data.frame(cramerschi.output.list, 
      contactxcert50, contactxcertmed, contactxcorr50, contactxcorrmed,
      fieldxcert50, fieldxcertmed, fieldxcorr50, fieldxcorrmed,
      collectxcert50, collectxcertmed, collectxcorr50, collectxcorrmed,
      handlexcert50, handlexcertmed, handlexcorr50, handlexcorrmed
)

View(fieldxknowcert)
```

# Opinion vs Knowledge and Certainty

Pprereq would not run as there was a difference in vector lengths

```{r}
#CWDAL
cwdalxcorrmed<-cramerschi(surv$CWDAL, surv$CORRECTmed)
     cwdalxcorr50<-cramerschi(surv$CWDAL, surv$CORRECT50)
     cwdalxcertmed<-cramerschi(surv$CWDAL, surv$CERTAINmed)
     cwdalxcert50<-cramerschi(surv$CWDAL, surv$CERTAIN50)

  #BATS
     batsxcorrmed<-cramerschi(surv$BATS, surv$CORRECTmed)
     batsxcorr50<-cramerschi(surv$BATS, surv$CORRECT50)
     batsxcertmed<-cramerschi(surv$BATS, surv$CERTAINmed)
     batsxcert50<-cramerschi(surv$BATS, surv$CERTAIN50)
     
#pprereq
     #pprereqxcorrmed<-cramerschi(surv$PPREREQ, surv$CORRECTmed)
     #pprereqxcorr50<-cramerschi(surv$PPREREQ, surv$CORRECT50)
     #pprereqxcertmed<-cramerschi(surv$PPREREQ, surv$CERTAINmed)
     #pprereqxcert50<-cramerschi(surv$PPREREQ, surv$CERTAIN50)
     
#EHD
     ehdxcorrmed<-cramerschi(surv$EHD, surv$CORRECTmed)
     ehdxcorr50<-cramerschi(surv$EHD, surv$CORRECT50)
     ehdxcertmed<-cramerschi(surv$EHD, surv$CERTAINmed)
     ehdxcert50<-cramerschi(surv$EHD, surv$CERTAIN50)
     
#DARWIN
     darwinxcorrmed<-cramerschi(surv$DARWIN, surv$CORRECTmed)
     darwinxcorr50<-cramerschi(surv$DARWIN, surv$CORRECT50)
     darwinxcertmed<-cramerschi(surv$DARWIN, surv$CERTAINmed)
     darwinxcert50<-cramerschi(surv$DARWIN, surv$CERTAIN50)
     
#popred
     popredxcorrmed<-cramerschi(surv$POPRED, surv$CORRECTmed)
     popredxcorr50<-cramerschi(surv$POPRED, surv$CORRECT50)
     popredxcertmed<-cramerschi(surv$POPRED, surv$CERTAINmed)
     popredxcert50<-cramerschi(surv$POPRED, surv$CERTAIN50)
     
#popplan
     popplanxcorrmed<-cramerschi(surv$POPPLAN, surv$CORRECTmed)
     popplanxcorr50<-cramerschi(surv$POPPLAN, surv$CORRECT50)
     popplanxcertmed<-cramerschi(surv$POPPLAN, surv$CERTAINmed)
     popplanxcert50<-cramerschi(surv$POPPLAN, surv$CERTAIN50)

#Survey
     surveyxcorrmed<-cramerschi(surv$SURVEY, surv$CORRECTmed)
     surveyxcorr50<-cramerschi(surv$SURVEY, surv$CORRECT50)
     surveyxcertmed<-cramerschi(surv$SURVEY, surv$CERTAINmed)
     surveyxcert50<-cramerschi(surv$SURVEY, surv$CERTAIN50)
    
#vaccine
     vaccinexcorrmed<-cramerschi(surv$VACCINE, surv$CORRECTmed)
     vaccinexcorr50<-cramerschi(surv$VACCINE, surv$CORRECT50)
     vaccinexcertmed<-cramerschi(surv$VACCINE, surv$CERTAINmed)
     vaccinexcert50<-cramerschi(surv$VACCINE, surv$CERTAIN50)

#preval
     prevalxcorrmed<-cramerschi(surv$PREVAL, surv$CORRECTmed)
     prevalxcorr50<-cramerschi(surv$PREVAL, surv$CORRECT50)
     prevalxcertmed<-cramerschi(surv$PREVAL, surv$CERTAINmed)
     prevalxcert50<-cramerschi(surv$PREVAL, surv$CERTAIN50)
     
#diverse
     diversexcorrmed<-cramerschi(surv$DIVERSE, surv$CORRECTmed)
     diversexcorr50<-cramerschi(surv$DIVERSE, surv$CORRECT50)
     diversexcertmed<-cramerschi(surv$DIVERSE, surv$CERTAINmed)
     diversexcert50<-cramerschi(surv$DIVERSE, surv$CERTAIN50)
     
#conseq
     conseqxcorrmed<-cramerschi(surv$CONSEQ, surv$CORRECTmed)
     conseqxcorr50<-cramerschi(surv$CONSEQ, surv$CORRECT50)
     conseqxcertmed<-cramerschi(surv$CONSEQ, surv$CERTAINmed)
     conseqxcert50<-cramerschi(surv$CONSEQ, surv$CERTAIN50)
     
#Climate
     climatexcorrmed<-cramerschi(surv$CLIMATE, surv$CORRECTmed)
     climatexcorr50<-cramerschi(surv$CLIMATE, surv$CORRECT50)
     climatexcertmed<-cramerschi(surv$CLIMATE, surv$CERTAINmed)
     climatexcert50<-cramerschi(surv$CLIMATE, surv$CERTAIN50)
     
#Edreq
     edreqxcorrmed<-cramerschi(surv$EDREQ, surv$CORRECTmed)
     edreqxcorr50<-cramerschi(surv$EDREQ, surv$CORRECT50)
     edreqxcertmed<-cramerschi(surv$EDREQ, surv$CERTAINmed)
     edreqxcert50<-cramerschi(surv$EDREQ, surv$CERTAIN50)
     
#INFO
     infoxcorrmed<-cramerschi(surv$INFO, surv$CORRECTmed)
     infoxcorr50<-cramerschi(surv$INFO, surv$CORRECT50)
     infoxcertmed<-cramerschi(surv$INFO, surv$CERTAINmed)
     infoxcert50<-cramerschi(surv$INFO, surv$CERTAIN50)
     
opinionxknowcert<-data.frame(cramerschi.output.list, 
     cwdalxcert50, cwdalxcertmed, cwdalxcorr50, cwdalxcorrmed,
     batsxcert50, batsxcertmed, batsxcorr50, batsxcorrmed,
     ehdxcert50, ehdxcertmed, ehdxcorr50, ehdxcorrmed,
     darwinxcert50, darwinxcertmed, darwinxcorr50, darwinxcorrmed,
     popredxcert50, popredxcertmed, popredxcorr50, popredxcorrmed,
     popplanxcert50, popplanxcertmed, popplanxcorr50, popplanxcorrmed,
     surveyxcert50, surveyxcertmed, surveyxcorr50, surveyxcorrmed,
     vaccinexcert50, vaccinexcertmed, vaccinexcorr50, vaccinexcorrmed,
     prevalxcert50, prevalxcertmed, prevalxcorr50, prevalxcorrmed,
     diversexcert50, diversexcertmed, diversexcorr50, diversexcorrmed,
     conseqxcert50, conseqxcertmed, conseqxcorr50, conseqxcorrmed,
     climatexcert50, climatexcertmed, climatexcorr50, climatexcorrmed,
     edreqxcert50, edreqxcertmed, edreqxcorr50, edreqxcorrmed,
     infoxcert50, infoxcertmed, infoxcorr50, infoxcorrmed
)                           

View( opinionxknowcert)
```

# Field and Hanlding vs PPE usages

```{r}
#contact
     contactxppe<-cramerschi(surv$CONTACT, surv$PPE)
     contactxppetime<-cramerschi(surv$CONTACT, surv$PPETIME)
  
     
     #field

     fieldxppe<-cramerschi(surv$FIELD, surv$PPE)
     fieldxppetime<-cramerschi(surv$FIELD, surv$PPETIME)
     
     #collect

     collectxppe<-cramerschi(surv$COLLECT, surv$PPE)
     collectxppetime<-cramerschi(surv$COLLECT, surv$PPETIME)
     
     #handle

     handlexppe<-cramerschi(surv$HANDLE, surv$PPE)
     handlexppetime<-cramerschi(surv$HANDLE, surv$PPETIME)
     
fieldxppe<-data.frame(cramerschi.output.list,      
        contactxppe, contactxppetime,
        fieldxppe, fieldxppetime,
        collectxppe, collectxppetime,
        handlexppe, handlexppetime
)     

View(fieldxppe)
```

# Knowledge vs Certainty

```{r}
#knowledge x certainty
     
     corrmedxcertmed<- cramerschi(surv$CORRECTmed, surv$CERTAINmed)
       corrmedxcert50<-cramerschi(surv$CORRECT50, surv$CERTAIN50)
       corr50xcert50<-cramerschi(surv$CORRECT50, surv$CERTAIN50)
       corr50xcertmed<-cramerschi(surv$CORRECT50, surv$CERTAINmed)
    
     knowledgexcert<-data.frame(cramerschi.output.list, 
                                corrmedxcert50, corrmedxcertmed,
                                corr50xcert50, corr50xcertmed
     )
View(knowledgexcert)     
```

# Write CSV

```{r}
#write csv

oup = file.path(analyses, "outputs")

write.csv(demoxknowcert, file.path(oup, "demographic_knowledge-certainty.csv"))
write.csv(eduxknowcert, file.path(oup, "education_knowledge-certainty.csv"))
write.csv(fieldxknowcert,file.path(oup, "field_knowledge-certainty.csv"))
write.csv(opinionxknowcert, file.path(oup, "opinion_knowledge-certainty.csv"))
write.csv(fieldxppe,file.path(oup, "field_ppe.csv"))
write.csv(knowledgexcert,file.path(oup, "knowledge_certainty.csv"))

```


# References Cited
### Packages

```{r bib}
#| echo: false

#### To write a bib file
# knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='pckg.bib')

#### to display the packages within the .qmd without creating another .bib ####
knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='')

```
