---
title: "KAP_analysis"
format: html
editor: visual
---

# Load data and create function

I essentially took Travis' script and made it into a function that will spit all of the outputs into a string for a column. in a summary table. In the output, there are for rows listed "zero_zero, zero_one, etc." this are as follows "column_row" or in terms of the variables in the function it is equivalent to "a_b".

```{r}
#load data
survdata <- read.csv("BinaryCombined.csv")
#View(survdata)

#load packages
library(rcompanion)
 
#create function to combine chi tests all at once
 cramerschi<-function(a,b){
   
   data.table <- table(a,b) 
   data.chi <- chisq.test(data.table)
   col_counts <- colSums(data.table)
   data.table_with_counts <- rbind(data.table, Col_Counts = col_counts)
   CramV<-as.numeric(cramerV(data.table))
  #assign outputs
    chistat<-as.numeric(data.chi$statistic)
   chi.df<-as.integer(data.chi$parameter)
   chi.pvalue<-data.chi$p.value
   zero_zero<-data.table_with_counts[1,1]
   zero_one<-data.table_with_counts[2,1]
   one_zero<-data.table_with_counts[1,2]
   one_one<-data.table_with_counts[2,2]
   colzerotot<-data.table_with_counts[3,1]
   colonetot<-data.table_with_counts[3,2]
   total.output<-c(chistat,chi.df, chi.pvalue, CramV, zero_zero, zero_one,
                           one_zero, one_one,colzerotot,colonetot)
  
   
   return(total.output)
 }
 
 
  #create vector of label for output string
cramerschi.output.list<-c("chistat","chi.df", "chi.pvalue", "CramV", "zero_zero", "zero_one",
                        "one_zero", "one_one","colzerotot","colonetot")


 #output will follow top row then first column of chiX table
 #X zeroone is the column "0" and the row "1"
 #columns will be second variable in comparison
 #rows will be first listed
 
```

# Manual comparison for output

This is just a visual of what the output would look like in a chi square table

```{r}
#Test comparison to compare to true ChiX table from degree x certain50
 
 
 
 data.table.test <- table(survdata$AGE, survdata$CORRECTmed)
 data.chi.test <- chisq.test(data.table.test)
 print(data.chi.test)
 col_counts.test <- colSums(data.table.test)
 col_counts.test
 data.table_with_counts.test <- rbind(data.table.test, Col_Counts = col_counts.test)
 print(data.table_with_counts.test)
 
 #compare this to
agexcorrmed<-cramerschi(survdata$AGE, survdata$CORRECTmed)
 data.frame(cramerschi.output.list,agexcorrmed)
```

# Demographic Information vs Knowledge and Certainty

```{r}
#in general we need to compare Demographic<->knowledge, Dem<->Certainty, Education<->{Knowledge,Certainty}
#Opinion<->{knowledge, certainty}, knowledge<->certainty
#the knowledge and certainty categories are summarized at the end to use in a 
#binary classification rather than put them all together
#maybe do handling and field work vs knowledge and cert
#handling and ppe

#Age
agexcorrmed<-cramerschi(survdata$AGE, survdata$CORRECTmed)
agexcorr50<-cramerschi(survdata$AGE, survdata$CORRECT50)
agexcertmed<-cramerschi(survdata$AGE, survdata$CERTAINmed)
agexcert50<-cramerschi(survdata$AGE, survdata$CERTAIN50)

#gender
genxcorrmed<-cramerschi(survdata$GENDER, survdata$CORRECTmed)
genxcorr50<-cramerschi(survdata$GENDER, survdata$CORRECT50)
genxcertmed<-cramerschi(survdata$GENDER, survdata$CERTAINmed)
genxcert50<-cramerschi(survdata$GENDER, survdata$CERTAIN50)

#income
incomexcorrmed<-cramerschi(survdata$INCOME, survdata$CORRECTmed)
incomexcorr50<-cramerschi(survdata$INCOME, survdata$CORRECT50)
incomexcertmed<- cramerschi(survdata$INCOME, survdata$CERTAINmed)
incomexcert50<-cramerschi(survdata$INCOME, survdata$CERTAIN50)


#age, gender, income
demoxknowcert<-data.frame(cramerschi.output.list, agexcert50, agexcertmed, agexcorr50, agexcorrmed,
 genxcert50, genxcertmed, genxcorr50, genxcorrmed,
 incomexcert50, incomexcertmed, incomexcorr50, incomexcorrmed
)

View(demoxknowcert)
```

# Education vs Knowledge and Certainty

```{r}
#degree
degreexcorrmed<-cramerschi(survdata$DEGREE, survdata$CORRECTmed)
degreexcorr50<-cramerschi(survdata$DEGREE,survdata$CORRECT50)
degreexcertmed<-cramerschi(survdata$DEGREE, survdata$CERTAINmed)
degreexcert50<-cramerschi(survdata$DEGREE, survdata$CERTAIN50)

#TWS
twsxcorrmed<-cramerschi(survdata$TWS, survdata$CORRECTmed)
twsxcorr50<- cramerschi(survdata$TWS, survdata$CORRECT50)
twsxcertmed<-cramerschi(survdata$TWS, survdata$CERTAINmed)
twsxcert50<-cramerschi(survdata$TWS, survdata$CERTAIN50)

#course
coursexcorrmed<-cramerschi(survdata$COURSE, survdata$CORRECTmed)
coursexcorr50<-cramerschi(survdata$COURSE, survdata$CORRECT50)
coursexcertmed<-cramerschi(survdata$COURSE, survdata$CERTAINmed)
coursexcert50<-cramerschi(survdata$COURSE, survdata$CERTAIN50)

#Selftitle
titlexcorrmed<-cramerschi(survdata$SELFTITLE, survdata$CORRECTmed)
titlexcorr50<-cramerschi(survdata$SELFTITLE, survdata$CORRECT50)
titlexcertmed<-cramerschi(survdata$SELFTITLE, survdata$CERTAINmed)
titlexcert50<-cramerschi(survdata$SELFTITLE, survdata$CERTAIN50)

#biotime
biotimexcorrmed<-cramerschi(survdata$BIOTIME, survdata$CORRECTmed)
biotimexcorr50<-cramerschi(survdata$BIOTIME, survdata$CORRECT50)
biotimexcertmed<-cramerschi(survdata$BIOTIME, survdata$CERTAINmed)
biotimexcert50<-cramerschi(survdata$BIOTIME, survdata$CERTAIN50)

#education
eduxcorrmed<-cramerschi(survdata$EDUCATION, survdata$CORRECTmed)
eduxcorr50<-cramerschi(survdata$EDUCATION, survdata$CORRECT50)
eduxcertmed<-cramerschi(survdata$EDUCATION, survdata$CERTAINmed)
eduxcert50<-cramerschi(survdata$EDUCATION, survdata$CERTAIN50)

#degree, tws, course, selftitle, biotime, education
eduxknowcert<-data.frame(cramerschi.output.list, 
      degreexcert50, degreexcertmed, degreexcorr50, degreexcorrmed,
      twsxcert50,twsxcertmed, twsxcorr50, twsxcorrmed,
      coursexcert50, coursexcertmed, coursexcorr50, coursexcorrmed,
      titlexcert50, titlexcertmed, titlexcorr50, titlexcorrmed,
      biotimexcert50, biotimexcertmed, biotimexcorr50, biotimexcorrmed,
      eduxcert50, eduxcertmed, eduxcorr50, eduxcorrmed
)
View(eduxknowcert)
```

# Field and Handling vs Knowledge and Certainty

```{r}
#contact
contactxcorrmed<-cramerschi(survdata$CONTACT, survdata$CORRECTmed)
contactxcorr50<-cramerschi(survdata$CONTACT, survdata$CORRECT50)
contactxcertmed<-cramerschi(survdata$CONTACT, survdata$CERTAINmed)
contactxcert50<-cramerschi(survdata$CONTACT, survdata$CERTAIN50)

#field
fieldxcorrmed<-cramerschi(survdata$FIELD, survdata$CORRECTmed)
fieldxcorr50<-cramerschi(survdata$FIELD, survdata$CORRECT50)
fieldxcertmed<-cramerschi(survdata$FIELD, survdata$CERTAINmed)
fieldxcert50<-cramerschi(survdata$FIELD, survdata$CERTAIN50)

#collect
collectxcorrmed<-cramerschi(survdata$COLLECT, survdata$CORRECTmed)
collectxcorr50<-cramerschi(survdata$COLLECT, survdata$CORRECT50)
collectxcertmed<-cramerschi(survdata$COLLECT, survdata$CERTAINmed)
collectxcert50<-cramerschi(survdata$COLLECT, survdata$CERTAIN50)

#handle
handlexcorrmed<-cramerschi(survdata$HANDLE, survdata$CORRECTmed)
handlexcorr50<-cramerschi(survdata$HANDLE, survdata$CORRECT50)
handlexcertmed<-cramerschi(survdata$HANDLE, survdata$CERTAINmed)
handlexcert50<-cramerschi(survdata$HANDLE, survdata$CERTAIN50)

#contact, field, collect, handle

fieldxknowcert<-data.frame(cramerschi.output.list, 
      contactxcert50, contactxcertmed, contactxcorr50, contactxcorrmed,
      fieldxcert50, fieldxcertmed, fieldxcorr50, fieldxcorrmed,
      collectxcert50, collectxcertmed, collectxcorr50, collectxcorrmed,
      handlexcert50, handlexcertmed, handlexcorr50, handlexcorrmed
)

View(fieldxknowcert)
```

# Opinion vs Knowledge and Certainty

Pprereq would not run as there was a difference in vector lengths

```{r}
#CWDAL
cwdalxcorrmed<-cramerschi(survdata$CWDAL, survdata$CORRECTmed)
     cwdalxcorr50<-cramerschi(survdata$CWDAL, survdata$CORRECT50)
     cwdalxcertmed<-cramerschi(survdata$CWDAL, survdata$CERTAINmed)
     cwdalxcert50<-cramerschi(survdata$CWDAL, survdata$CERTAIN50)

  #BATS
     batsxcorrmed<-cramerschi(survdata$BATS, survdata$CORRECTmed)
     batsxcorr50<-cramerschi(survdata$BATS, survdata$CORRECT50)
     batsxcertmed<-cramerschi(survdata$BATS, survdata$CERTAINmed)
     batsxcert50<-cramerschi(survdata$BATS, survdata$CERTAIN50)
     
#pprereq
     #pprereqxcorrmed<-cramerschi(survdata$PPREREQ, survdata$CORRECTmed)
     #pprereqxcorr50<-cramerschi(survdata$PPREREQ, survdata$CORRECT50)
     #pprereqxcertmed<-cramerschi(survdata$PPREREQ, survdata$CERTAINmed)
     #pprereqxcert50<-cramerschi(survdata$PPREREQ, survdata$CERTAIN50)
     
#EHD
     ehdxcorrmed<-cramerschi(survdata$EHD, survdata$CORRECTmed)
     ehdxcorr50<-cramerschi(survdata$EHD, survdata$CORRECT50)
     ehdxcertmed<-cramerschi(survdata$EHD, survdata$CERTAINmed)
     ehdxcert50<-cramerschi(survdata$EHD, survdata$CERTAIN50)
     
#DARWIN
     darwinxcorrmed<-cramerschi(survdata$DARWIN, survdata$CORRECTmed)
     darwinxcorr50<-cramerschi(survdata$DARWIN, survdata$CORRECT50)
     darwinxcertmed<-cramerschi(survdata$DARWIN, survdata$CERTAINmed)
     darwinxcert50<-cramerschi(survdata$DARWIN, survdata$CERTAIN50)
     
#popred
     popredxcorrmed<-cramerschi(survdata$POPRED, survdata$CORRECTmed)
     popredxcorr50<-cramerschi(survdata$POPRED, survdata$CORRECT50)
     popredxcertmed<-cramerschi(survdata$POPRED, survdata$CERTAINmed)
     popredxcert50<-cramerschi(survdata$POPRED, survdata$CERTAIN50)
     
#popplan
     popplanxcorrmed<-cramerschi(survdata$POPPLAN, survdata$CORRECTmed)
     popplanxcorr50<-cramerschi(survdata$POPPLAN, survdata$CORRECT50)
     popplanxcertmed<-cramerschi(survdata$POPPLAN, survdata$CERTAINmed)
     popplanxcert50<-cramerschi(survdata$POPPLAN, survdata$CERTAIN50)

#Survey
     surveyxcorrmed<-cramerschi(survdata$SURVEY, survdata$CORRECTmed)
     surveyxcorr50<-cramerschi(survdata$SURVEY, survdata$CORRECT50)
     surveyxcertmed<-cramerschi(survdata$SURVEY, survdata$CERTAINmed)
     surveyxcert50<-cramerschi(survdata$SURVEY, survdata$CERTAIN50)
    
#vaccine
     vaccinexcorrmed<-cramerschi(survdata$VACCINE, survdata$CORRECTmed)
     vaccinexcorr50<-cramerschi(survdata$VACCINE, survdata$CORRECT50)
     vaccinexcertmed<-cramerschi(survdata$VACCINE, survdata$CERTAINmed)
     vaccinexcert50<-cramerschi(survdata$VACCINE, survdata$CERTAIN50)

#preval
     prevalxcorrmed<-cramerschi(survdata$PREVAL, survdata$CORRECTmed)
     prevalxcorr50<-cramerschi(survdata$PREVAL, survdata$CORRECT50)
     prevalxcertmed<-cramerschi(survdata$PREVAL, survdata$CERTAINmed)
     prevalxcert50<-cramerschi(survdata$PREVAL, survdata$CERTAIN50)
     
#diverse
     diversexcorrmed<-cramerschi(survdata$DIVERSE, survdata$CORRECTmed)
     diversexcorr50<-cramerschi(survdata$DIVERSE, survdata$CORRECT50)
     diversexcertmed<-cramerschi(survdata$DIVERSE, survdata$CERTAINmed)
     diversexcert50<-cramerschi(survdata$DIVERSE, survdata$CERTAIN50)
     
#conseq
     conseqxcorrmed<-cramerschi(survdata$CONSEQ, survdata$CORRECTmed)
     conseqxcorr50<-cramerschi(survdata$CONSEQ, survdata$CORRECT50)
     conseqxcertmed<-cramerschi(survdata$CONSEQ, survdata$CERTAINmed)
     conseqxcert50<-cramerschi(survdata$CONSEQ, survdata$CERTAIN50)
     
#Climate
     climatexcorrmed<-cramerschi(survdata$CLIMATE, survdata$CORRECTmed)
     climatexcorr50<-cramerschi(survdata$CLIMATE, survdata$CORRECT50)
     climatexcertmed<-cramerschi(survdata$CLIMATE, survdata$CERTAINmed)
     climatexcert50<-cramerschi(survdata$CLIMATE, survdata$CERTAIN50)
     
#Edreq
     edreqxcorrmed<-cramerschi(survdata$EDREQ, survdata$CORRECTmed)
     edreqxcorr50<-cramerschi(survdata$EDREQ, survdata$CORRECT50)
     edreqxcertmed<-cramerschi(survdata$EDREQ, survdata$CERTAINmed)
     edreqxcert50<-cramerschi(survdata$EDREQ, survdata$CERTAIN50)
     
#INFO
     infoxcorrmed<-cramerschi(survdata$INFO, survdata$CORRECTmed)
     infoxcorr50<-cramerschi(survdata$INFO, survdata$CORRECT50)
     infoxcertmed<-cramerschi(survdata$INFO, survdata$CERTAINmed)
     infoxcert50<-cramerschi(survdata$INFO, survdata$CERTAIN50)
     
opinionxknowcert<-data.frame(cramerschi.output.list, 
     cwdalxcert50, cwdalxcertmed, cwdalxcorr50, cwdalxcorrmed,
     batsxcert50, batsxcertmed, batsxcorr50, batsxcorrmed,
     ehdxcert50, ehdxcertmed, ehdxcorr50, ehdxcorrmed,
     darwinxcert50, darwinxcertmed, darwinxcorr50, darwinxcorrmed,
     popredxcert50, popredxcertmed, popredxcorr50, popredxcorrmed,
     popplanxcert50, popplanxcertmed, popplanxcorr50, popplanxcorrmed,
     surveyxcert50, surveyxcertmed, surveyxcorr50, surveyxcorrmed,
     vaccinexcert50, vaccinexcertmed, vaccinexcorr50, vaccinexcorrmed,
     prevalxcert50, prevalxcertmed, prevalxcorr50, prevalxcorrmed,
     diversexcert50, diversexcertmed, diversexcorr50, diversexcorrmed,
     conseqxcert50, conseqxcertmed, conseqxcorr50, conseqxcorrmed,
     climatexcert50, climatexcertmed, climatexcorr50, climatexcorrmed,
     edreqxcert50, edreqxcertmed, edreqxcorr50, edreqxcorrmed,
     infoxcert50, infoxcertmed, infoxcorr50, infoxcorrmed
)                           

View( opinionxknowcert)
```

# Field and Hanlding vs PPE usages

```{r}
#contact
     contactxppe<-cramerschi(survdata$CONTACT, survdata$PPE)
     contactxppetime<-cramerschi(survdata$CONTACT, survdata$PPETIME)
  
     
     #field

     fieldxppe<-cramerschi(survdata$FIELD, survdata$PPE)
     fieldxppetime<-cramerschi(survdata$FIELD, survdata$PPETIME)
     
     #collect

     collectxppe<-cramerschi(survdata$COLLECT, survdata$PPE)
     collectxppetime<-cramerschi(survdata$COLLECT, survdata$PPETIME)
     
     #handle

     handlexppe<-cramerschi(survdata$HANDLE, survdata$PPE)
     handlexppetime<-cramerschi(survdata$HANDLE, survdata$PPETIME)
     
fieldxppe<-data.frame(cramerschi.output.list,      
        contactxppe, contactxppetime,
        fieldxppe, fieldxppetime,
        collectxppe, collectxppetime,
        handlexppe, handlexppetime
)     

View(fieldxppe)
```

# Knowledge vs Certainty

```{r}
#knowledge x certainty
     
     corrmedxcertmed<- cramerschi(survdata$CORRECTmed, survdata$CERTAINmed)
       corrmedxcert50<-cramerschi(survdata$CORRECT50, survdata$CERTAIN50)
       corr50xcert50<-cramerschi(survdata$CORRECT50, survdata$CERTAIN50)
       corr50xcertmed<-cramerschi(survdata$CORRECT50, survdata$CERTAINmed)
    
     knowledgexcert<-data.frame(cramerschi.output.list, 
                                corrmedxcert50, corrmedxcertmed,
                                corr50xcert50, corr50xcertmed
     )
View(knowledgexcert)     
```

# Write CSV

```{r}
#write csv


write.csv(demoxknowcert, "demographic_knowledge-certainty.csv")
write.csv(eduxknowcert, "education_knowledge-certainty.csv")
write.csv(fieldxknowcert, "field_knowledge-certainty.csv")
write.csv(opinionxknowcert, "opinion_knowledge-certainty.csv")
write.csv(fieldxppe, "field_ppe.csv")
write.csv(knowledgexcert, "knowledge_certainty.csv")

```
