---
title: "Descriptive Statistics"
output: html_notebook
---
#### Packages & Data
```{r}

require(dplyr)
require(sf)
require(sp)
require(tidyverse)
require(tidyterra)
require(terra)
require(ggplot2)

# completed/ full responses = 154
surv = read.csv("C:/Users/rylee/Box/Wildlife Health Survey/Analysis/Data/Descriptive/hsurvcomplete.csv")

# partial responses = 126
survp = read.csv("C:/Users/rylee/Box/Wildlife Health Survey/Analysis/Data/Descriptive/hsurvpart.csv")

```

#### Processing Responses
```{r}

# Removing rows where survey population requirements are not met (age/residency)
survp = survp %>%
  filter(DOB != "" & RESIDENT != "") # 70 responses remaining 

survp = survp %>%
  filter(`COMPLETE` >= 50) # 9 Observations remaining 

# calculating age (complete and partial)
survp$AGE = 2024 - survp$DOB
surv$AGE = 2024 - surv$DOB

# combining datasets = 163 total
surv = rbind(surv, survp)

```

# DESCRIPTIVE STATISTICS

# Spatial Proximity 
#### ZIPCODE
**What is the zip code of your current residence? (5-digit zip code)**
```{r}
```

#### COUNTIES
**In which counties do you regularly come into contact with wildlife in Alabama? **
*Number of Respondents Selected / Options*
```{r}

splitCOUNTIES = surv %>%
  separate_rows(COUNTIES, sep = ",") %>%
  mutate(COUNTIES = trimws(COUNTIES))

totCOUNTIES = nrow(splitCOUNTIES)

responseCOUNTIES = splitCOUNTIES %>%
    count(COUNTIES) %>%
    rename(count = n) %>%
  mutate(proportion = count / totCOUNTIES)

sum(responseCOUNTIES$proportion)
responseCOUNTIES

```

*Number of Response Options Selected / Respondent*
```{r}

splitCOUNTIES = surv %>%
  mutate(optionsCOUNTIES = str_count(COUNTIES, ",") + 1)

COUNTIES = surv$COUNTIES
COUNTIES = na.omit(COUNTIES)
COUNTIES = COUNTIES[COUNTIES != ""]

optionsCOUNTIES = splitCOUNTIES %>%
  count(optionsCOUNTIES) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COUNTIES))

sum(optionsCOUNTIES$proportion)
optionsCOUNTIES

optionssumCOUNTIES = optionsCOUNTIES %>%
  summarise(
    mean = mean(optionsCOUNTIES, na.rm = TRUE),
    sd = sd(optionsCOUNTIES, na.rm = TRUE),
    median = median(optionsCOUNTIES, na.rm = TRUE),
    mode = as.numeric(names(sort(table(optionsCOUNTIES), decreasing = TRUE)[1])))

optionssumCOUNTIES

```


# Demographics 
#### AGE & GENDER
```{r}

responsesumAGE = surv %>%
  summarise(
    mean = mean(AGE, na.rm = TRUE),
    sd = sd(AGE, na.rm = TRUE),
    median = median(AGE, na.rm = TRUE),
    mode = as.numeric(names(sort(table(AGE), decreasing = TRUE)[1])),
    min = min(AGE, na.rm = TRUE),
    max = max(AGE, na.rm = TRUE))

responsesumAGE


###############################################################################

GENDER = surv$GENDER
GENDER = na.omit(GENDER)
GENDER = GENDER[GENDER != ""]


optionsGENDER = surv %>%
  count(surv$GENDER) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(GENDER))

sum(optionsGENDER$proportion)
optionsGENDER

```

#### RACE & ETHNICITY
```{r}

RACE = surv$RACE
RACE = na.omit(RACE)
RACE = RACE[RACE != ""]

optionsRACE = surv %>%
  count(surv$RACE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(RACE))

sum(optionsRACE$proportion)
optionsRACE

###############################################################################

ETHNICITY = surv$ETHNICITY
ETHNICITY = na.omit(ETHNICITY)
ETHNICITY = ETHNICITY[ETHNICITY != ""]

optionsETHNICITY = surv %>%
  count(surv$ETHNICITY) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(ETHNICITY))

sum(optionsETHNICITY$proportion)
optionsETHNICITY


```

#### INCOME
**What was your approximate household income in 2023?**
```{r}

INCOME = surv$INCOME
INCOME = na.omit(INCOME)
INCOME = INCOME[INCOME != ""]

optionsINCOME = surv %>%
  count(surv$INCOME) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(INCOME))

sum(optionsINCOME$proportion)
optionsINCOME


```


#### AFFILIATE
**What is your primary affiliation in the field of wildlife biology?**
```{r}

AFFILIATE = surv$AFFILIATE
AFFILIATE = na.omit(AFFILIATE)
AFFILIATE = AFFILIATE[AFFILIATE != ""]

optionsAFFILIATE = surv %>%
  count(surv$AFFILIATE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(AFFILIATE))

sum(optionsAFFILIATE$proportion)
optionsAFFILIATE

```


#### ACTIVITY
**Which type of activities best describe the primary focus of your work in wildlife biology?**
```{r}

ACTIVITY = surv$ACTIVITY
ACTIVITY = na.omit(ACTIVITY)
ACTIVITY = ACTIVITY[ACTIVITY != ""]

optionsACTIVITY = surv %>%
  count(surv$ACTIVITY) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(ACTIVITY))

sum(optionsACTIVITY$proportion)
optionsACTIVITY

```

#### SOURCE
**What is your preferred source to obtain information regarding wildlife health in Alabama? **
*Number of Respondents Selected / Options*
```{r}

splitSOURCE = surv  %>%
  separate_rows(SOURCE, sep = ",") %>%
  mutate(SOURCE = trimws(SOURCE))

responseSOURCE = splitSOURCE %>%
    count(SOURCE) %>%
  rename(count = n) %>%
  mutate(proportion = count / nrow(splitSOURCE))

sum(responseSOURCE$proportion)
responseSOURCE

```

*Number of Response Options Selected / Respondent*
```{r}

splitSOURCE = surv %>%
  mutate(optionsSOURCE = str_count(SOURCE, ",") + 1)

SOURCE = surv$SOURCE
SOURCE = na.omit(SOURCE)
SOURCE = SOURCE[SOURCE != ""]

optionsSOURCE = splitSOURCE %>%
  count(optionsSOURCE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(SOURCE))

sum(optionsSOURCE$proportion)
optionsSOURCE

optionssumSOURCE = optionsSOURCE %>%
  summarise(
    mean = mean(optionsSOURCE, na.rm = TRUE),
    sd = sd(optionsSOURCE, na.rm = TRUE),
    median = median(optionsSOURCE, na.rm = TRUE),
    mode = as.numeric(names(sort(table(optionsSOURCE), decreasing = TRUE)[1])))

optionssumSOURCE

```


# AU Wildlife Health Outreach - Symposium/Course
#### ACCESS
**Is the information you need regarding wildlife health in Alabama easily accessible to you?**
```{r}

ACCESS = surv$ACCESS
ACCESS = na.omit(ACCESS)
ACCESS = ACCESS[ACCESS != ""]

optionsACCESS = surv %>%
  count(surv$ACCESS) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(ACCESS))

sum(optionsACCESS$proportion)
optionsACCESS


```


#### INTEREST
**Would you be interested in learning more about wildlife health in Alabama?**
```{r}

INTEREST = surv$INTEREST
INTEREST = na.omit(INTEREST)
INTEREST = INTEREST[INTEREST != ""]

optionsINTEREST = surv %>%
  count(surv$INTEREST) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(INTEREST))

sum(optionsINTEREST$proportion)
optionsINTEREST

```


#### FREEINFO
**If there was a free course on wildlife health in Alabama, how would you like to participate? **
*Number of Respondents Selected / Options*
```{r}

splitFREEINFO = surv  %>%
  separate_rows(FREEINFO, sep = ",") %>%
  mutate(FREEINFO = trimws(FREEINFO))

responseFREEINFO = splitFREEINFO %>%
    count(FREEINFO) %>%
  rename(count = n) %>%
  mutate(proportion = count / nrow(splitFREEINFO))

sum(responseFREEINFO$proportion)
responseFREEINFO

```

*Number of Response Options Selected / Respondent*
```{r}

splitFREEINFO = surv %>%
  mutate(optionsFREEINFO = str_count(FREEINFO, ",") + 1)

FREEINFO = surv$FREEINFO
FREEINFO = na.omit(FREEINFO)
FREEINFO = FREEINFO[FREEINFO != ""]

optionsFREEINFO = splitFREEINFO %>%
  count(optionsFREEINFO) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(FREEINFO))

sum(optionsFREEINFO$proportion)
optionsFREEINFO

optionssumFREEINFO = optionsFREEINFO %>%
  summarise(
    mean = mean(optionsFREEINFO, na.rm = TRUE),
    sd = sd(optionsFREEINFO, na.rm = TRUE),
    median = median(optionsFREEINFO, na.rm = TRUE),
    mode = as.numeric(names(sort(table(optionsFREEINFO), decreasing = TRUE)[1])))

optionssumFREEINFO

```


#### TOPICS
**What TOPICS would you like to obtain more information regarding wildlife health in Alabama?**
*Number of Respondents Selected / Options*
```{r}

splitTOPICS = surv  %>%
  separate_rows(TOPICS, sep = ",") %>%
  mutate(TOPICS = trimws(TOPICS))

TOPICS = na.omit(splitTOPICS)
totTOPICS = length(TOPICS)

responseTOPICS = splitTOPICS %>%
    count(TOPICS) %>%
  rename(count = n) %>%
  mutate(proportion = count / nrow(splitTOPICS))

sum(responseTOPICS$proportion)
responseTOPICS

```

*Number of Response Options Selected / Respondent*
```{r}

splitTOPICS = surv %>%
  mutate(optionsTOPICS = str_count(TOPICS, ",") + 1)

TOPICS = surv$TOPICS
TOPICS = na.omit(TOPICS)
TOPICS = TOPICS[TOPICS != ""]

optionsTOPICS = splitTOPICS %>%
  count(optionsTOPICS) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(TOPICS))

sum(optionsTOPICS$proportion)
optionsTOPICS

optionssumTOPICS = optionsTOPICS %>%
  summarise(
    mean = mean(optionsTOPICS, na.rm = TRUE),
    sd = sd(optionsTOPICS, na.rm = TRUE),
    median = median(optionsTOPICS, na.rm = TRUE),
    mode = as.numeric(names(sort(table(optionsTOPICS), decreasing = TRUE)[1])))

optionssumTOPICS

```




# Education & Experience
#### EDUCATION
**What is the highest degree or level of education you have completed?**
```{r}

EDUCATION = surv$EDUCATION
EDUCATION = na.omit(EDUCATION)
EDUCATION = EDUCATION[EDUCATION != ""]

optionsEDUCATION = surv %>%
  count(surv$EDUCATION) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(EDUCATION))

sum(optionsEDUCATION$proportion)
optionsEDUCATION

```


#### DEGREE
**Do you have a degree in wildlife biology, ecology, or management or related field?**
```{r}

DEGREE = surv$DEGREE
DEGREE = na.omit(DEGREE)
DEGREE = DEGREE[DEGREE != ""]

optionsDEGREE = surv %>%
  count(surv$DEGREE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(DEGREE))

sum(optionsDEGREE$proportion)
optionsDEGREE

```


#### COURSE & COURSETIME
**Have you had a formal course on wildlife health? - When did you take a formal course on wildlife health?**
```{r}

COURSE = surv$COURSE
COURSE = na.omit(COURSE)
COURSETIME = COURSE[COURSE != ""]

optionsCOURSE = surv %>%
  count(surv$COURSE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COURSE))

sum(optionsCOURSE$proportion)
optionsCOURSE

###############################################################################

COURSETIME = surv$COURSETIME
COURSETIME = na.omit(COURSETIME)
COURSETIME = COURSETIME[COURSETIME != ""]

optionsCOURSETIME = surv %>%
  count(surv$COURSETIME) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COURSETIME))

sum(optionsCOURSETIME$proportion)
optionsCOURSETIME


```


#### BIOTIME
**For how many years have you been employed as a wildlife biologist?**
```{r}

BIOTIME = surv$BIOTIME
BIOTIME = na.omit(BIOTIME)
BIOTIME = BIOTIME[BIOTIME != ""]

optionsBIOTIME = surv %>%
  count(surv$BIOTIME) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(BIOTIME))

sum(optionsBIOTIME$proportion)
optionsBIOTIME


```



# Titles 
#### TWS
**Are you certified by The Wildlife Society (TWS) as a wildlife biologist?**
```{r}

TWS = surv$TWS
TWS = na.omit(TWS)
TWS = TWS[TWS != ""]

optionsTWS = surv %>%
  count(surv$TWS) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(TWS))

sum(optionsTWS$proportion)
optionsTWS

```


#### SELFTITLE
**Do you consider yourself to be a wildlife biologist?**
```{r}

SELFTITLE = surv$SELFTITLE
SELFTITLE = na.omit(SELFTITLE)
SELFTITLE = SELFTITLE[SELFTITLE != ""]

optionsSELFTITLE = surv %>%
  count(surv$SELFTITLE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(SELFTITLE))

sum(optionsSELFTITLE$proportion)
optionsSELFTITLE

```


#### LICENSE
**Did you have a hunting/trapping license for the state of Alabama in the past three years (2020-2023)?**
```{r}

LICENSE = surv$LICENSE
LICENSE = na.omit(LICENSE)
LICENSE = LICENSE[LICENSE != ""]

optionsLICENSE = surv %>%
  count(surv$LICENSE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(LICENSE))

sum(optionsLICENSE$proportion)
optionsLICENSE

```




# Practices 

## Direct & Indirect Contact
#### CONTACT
**How frequently do you come into direct physical contact with wildlife in Alabama as part of your employment duties?**
```{r}

CONTACT = surv$CONTACT
CONTACT = na.omit(CONTACT)
CONTACT = CONTACT[CONTACT != ""]

optionsCONTACT = surv %>%
  count(surv$CONTACT) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(CONTACT))

sum(optionsCONTACT$proportion)
optionsCONTACT


```

#### FIELD
**What percentage of the time do you spend in the field as part of your employment duties?**
```{r}

FIELD = surv$FIELD
FIELD = na.omit(FIELD)
FIELD = FIELD[FIELD != ""]

optionsFIELD = surv %>%
  count(surv$FIELD) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(FIELD))

sum(optionsFIELD$proportion)
optionsFIELD



responsesumFIELD = surv %>%
  summarise(
    mean = mean(FIELD, na.rm = TRUE),
    sd = sd(FIELD, na.rm = TRUE),
    median = median(FIELD, na.rm = TRUE),
    mode = as.numeric(names(sort(table(FIELD), decreasing = TRUE)[1])))

responsesumFIELD

```


#### COLLECT
**Do you regularly collect samples in the field from wildlife in Alabama?**
```{r}

COLLECT = surv$COLLECT
COLLECT = na.omit(COLLECT)
COLLECT = COLLECT[COLLECT != ""]

optionsCOLLECT = surv %>%
  count(surv$COLLECT) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COLLECT))

sum(optionsCOLLECT$proportion)
optionsCOLLECT


```


#### HANDLE & STATE
**Do you regularly handle samples in the laboratory or field that have been collected from wildlife in Alabama? - At collection of samples, the animal is? **
```{r}

HANDLE = surv$HANDLE
HANDLE = na.omit(HANDLE)
HANDLE = HANDLE[HANDLE != ""]

optionsHANDLE = surv %>%
  count(surv$HANDLE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(HANDLE))

sum(optionsHANDLE$proportion)
optionsHANDLE

###############################################################################

STATE = surv$STATE
STATE = na.omit(STATE)
STATE = STATE[STATE != ""]

optionsSTATE = surv %>%
  count(surv$STATE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(STATE))

sum(optionsSTATE$proportion)
optionsSTATE


```


## Precautions
#### PPE & PPETIME
**If you handle or collect samples from wildlife in Alabama, do you utilize personal protective equipment (PPE)? - How often do you use PPE when handling or collecting samples?**
```{r}

PPE = surv$PPE
PPE = na.omit(PPE)
PPE = PPE[PPE != ""]

optionsPPE = surv %>%
  count(surv$PPE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(PPE))

sum(optionsPPE$proportion)
optionsPPE

###############################################################################

PPETIME = surv$PPETIME
PPETIME = na.omit(PPETIME)
PPETIME = PPETIME[PPETIME != ""]

optionsPPETIME = surv %>%
  count(surv$PPETIME) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(PPETIME))

sum(optionsPPETIME$proportion)
optionsPPETIME


```



# Knowledge

## Transmission
#### PIGS
**Wild pigs may serve as a source of infectious disease transmission to both humans and domestic animals in Alabama**
```{r}

PIGS = surv$PIGS
PIGS = na.omit(PIGS)
PIGS = PIGS[PIGS != ""]

optionsPIGS = surv %>%
  count(surv$PIGS) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(PIGS))

sum(optionsPIGS$proportion)
optionsPIGS

```


#### CWD
**Chronic Wasting Disease (CWD) is primarily transmitted among cervids (deer/elk) through ticks**
```{r}

CWD = surv$CWD
CWD = na.omit(CWD)
CWD = CWD[CWD != ""]

optionsCWD = surv %>%
  count(surv$CWD) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(CWD))

sum(optionsCWD$proportion)
optionsCWD


```


#### COVID
**SARS CoV2 (COVID) can infect deer**
```{r}

COVID = surv$COVID
COVID = na.omit(COVID)
COVID = COVID[COVID != ""]

optionsCOVID = surv %>%
  count(surv$COVID) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COVID))

sum(optionsCOVID$proportion)
optionsCOVID


```


#### COVIDSPILL
**SARS CoV2 (COVID) from wildlife can infect humans**
```{r}

COVIDSPILL = surv$COVIDSPILL
COVIDSPILL = na.omit(COVIDSPILL)
COVIDSPILL = COVIDSPILL[COVIDSPILL != ""]

optionsCOVIDSPILL = surv %>%
  count(surv$COVIDSPILL) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(COVIDSPILL))

sum(optionsCOVIDSPILL$proportion)
optionsCOVIDSPILL


```


#### RABIES 
**How is rabies transmitted?**
```{r}

RABIES = surv$RABIES
RABIES = na.omit(RABIES)
RABIES = RABIES[RABIES != ""]

optionsRABIES = surv %>%
  count(surv$RABIES) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(RABIES))

sum(optionsRABIES$proportion)
optionsRABIES

```


## Etiology
#### BRUCE
**Brucellosis affects reproduction in domestic animals but is not a concern for wildlife**
```{r}

BRUCE = surv$BRUCE
BRUCE = na.omit(BRUCE)
BRUCE = BRUCE[BRUCE != ""]

optionsBRUCE = surv %>%
  count(surv$BRUCE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(BRUCE))

sum(optionsBRUCE$proportion)
optionsBRUCE

```

#### FLU
**Avian influenza does not kill wildlife**
```{r}

FLU = surv$FLU
FLU = na.omit(FLU)
FLU = FLU[FLU != ""]

optionsFLU = surv %>%
  count(surv$FLU) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(FLU))

sum(optionsFLU$proportion)
optionsFLU


```


## Epidemiology
#### FLUAL
**Avian influenza has been found in wild and domestic birds in Alabama**
```{r}

FLUAL = surv$FLUAL
FLUAL = na.omit(FLUAL)
FLUAL = FLUAL[FLUAL != ""]

optionsFLUAL = surv %>%
  count(surv$FLUAL) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(FLUAL))

sum(optionsFLUAL$proportion)
optionsFLUAL


```


#### RABIESAL
**Rabies has been found in ALL states that border Alabama**
```{r}

RABIESAL = surv$RABIESAL
RABIESAL = na.omit(RABIESAL)
RABIESAL = RABIESAL[RABIESAL != ""]

optionsRABIESAL = surv %>%
  count(surv$RABIESAL) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(RABIESAL))

sum(optionsRABIESAL$proportion)
optionsRABIESAL


```


## Exposure Response
#### TURKEY
**How should you dispose of a fresh wild turkey carcass that was found in Alabama?**
```{r}

TURKEY = surv$TURKEY
TURKEY = na.omit(TURKEY)
TURKEY = TURKEY[TURKEY != ""]

optionsTURKEY = surv %>%
  count(surv$TURKEY) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(TURKEY))

sum(optionsTURKEY$proportion)
optionsTURKEY


```



# Attitudes 

## Perception of Risks
#### CWDAL
**CWD was present in Alabama before the 21st century**
```{r}

CWDAL = surv$CWDAL
CWDAL = na.omit(CWDAL)
CWDAL = CWDAL[CWDAL != ""]

optionsCWDAL = surv %>%
  count(surv$CWDAL) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(CWDAL))

sum(optionsCWDAL$proportion)
optionsCWDAL


```


#### BATS 
**Bats are significant carriers of many infectious diseases in Alabama**
```{r}

BATS = surv$BATS
BATS = na.omit(BATS)
BATS = BATS[BATS != ""]

optionsBATS = surv %>%
  count(surv$BATS) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(BATS))

sum(optionsBATS$proportion)
optionsBATS


```


#### PPEREQ
**Personal Protective Equipment (PPE) is necessary when conducting fieldwork that does not directly involve zoonotic diseases**
```{r}

PPEREQ = surv$PPEREQ
PPEREQ = na.omit(PPEREQ)
PPEREQ = PPEREQ[PPEREQ != ""]

optionsPPEREQ = surv %>%
  count(surv$PPEREQ) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(PPEREQ))

sum(optionsPPEREQ$proportion)
optionsPPEREQ


```


#### EHD
**Epizootic Hemorrhagic Disease (EHD) is a major threat to human health.**
```{r}

EHD = surv$EHD
EHD = na.omit(EHD)
EHD = EHD[EHD != ""]

optionsEHD = surv %>%
  count(surv$EHD) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(EHD))

sum(optionsEHD$proportion)
optionsEHD


```


## Disease Management
#### DARWIN
**The only way to deal with zoonotic diseases in wildlife (such as rabies) is to let nature take its course**
```{r}

DARWIN = surv$DARWIN
DARWIN = na.omit(DARWIN)
DARWIN = DARWIN[DARWIN != ""]

optionsDARWIN = surv %>%
  count(surv$DARWIN) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(DARWIN))

sum(optionsDARWIN$proportion)
optionsDARWIN


```


#### POPRED
**Reducing the population of certain wild species in affected areas will eliminate infectious diseases in Alabama**
```{r}

POPRED = surv$POPRED
POPRED = na.omit(POPRED)
POPRED = POPRED[POPRED != ""]

optionsPOPRED = surv %>%
  count(surv$POPRED) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(POPRED))

sum(optionsPOPRED$proportion)
optionsPOPRED


```


#### POPPLAN
**Current plans to manage wildlife populations in Alabama will be effective in controlling infectious diseases**
```{r}

POPPLAN = surv$POPPLAN
POPPLAN = na.omit(POPPLAN)
POPPLAN = POPPLAN[POPPLAN != ""]

optionsPOPPLAN = surv %>%
  count(surv$POPPLAN) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(POPPLAN))

sum(optionsPOPPLAN$proportion)
optionsPOPPLAN


```


#### SURVEY
**Surveillance is essential to successful infectious disease management**
```{r}

SURVEY = surv$SURVEY
SURVEY = na.omit(SURVEY)
SURVEY = SURVEY[SURVEY != ""]

optionsSURVEY = surv %>%
  count(surv$SURVEY) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(SURVEY))

sum(optionsSURVEY$proportion)
optionsSURVEY

```


#### VACCINE
**The vaccination of wildlife, such as for rabies, should be considered for other diseases**
```{r}

VACCINE = surv$VACCINE
VACCINE = na.omit(VACCINE)
VACCINE = VACCINE[VACCINE != ""]

optionsVACCINE = surv %>%
  count(surv$VACCINE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(VACCINE))

sum(optionsVACCINE$proportion)
optionsVACCINE


```


## Impacted Health
#### PREVAL
**about the current prevalence of wildlife diseases in Alabama**
```{r}

PREVAL = surv$PREVAL
PREVAL = na.omit(PREVAL)
PREVAL = PREVAL[PREVAL != ""]

optionsPREVAL = surv %>%
  count(surv$PREVAL) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(PREVAL))

sum(optionsPREVAL$proportion)
optionsPREVAL


```


#### DIVERSE
**that infectious diseases will affect Alabama’s biodiversity**
```{r}

DIVERSE = surv$DIVERSE
DIVERSE = na.omit(DIVERSE)
DIVERSE = DIVERSE[DIVERSE != ""]

optionsDIVERSE = surv %>%
  count(surv$DIVERSE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(DIVERSE))

sum(optionsDIVERSE$proportion)
optionsDIVERSE


```


#### CONSEQ
**that wildlife diseases in my region will affect my health or my family’s health today**
```{r}

CONSEQ = surv$CONSEQ
CONSEQ = na.omit(CONSEQ)
CONSEQ = CONSEQ[CONSEQ != ""]

optionsCONSEQ = surv %>%
  count(surv$CONSEQ) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(CONSEQ))

sum(optionsCONSEQ$proportion)
optionsCONSEQ


```


#### CLIMATE
**that climate change will impact wildlife health in Alabama.**
```{r}

CLIMATE = surv$CLIMATE
CLIMATE = na.omit(CLIMATE)
CLIMATE = CLIMATE[CLIMATE != ""]

optionsCLIMATE = surv %>%
  count(surv$CLIMATE) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(CLIMATE))

sum(optionsCLIMATE$proportion)
optionsCLIMATE


```


## Health Education
#### EDREQ
**A course on wildlife health should be required for a major in wildlife biology**
```{r}

EDREQ = surv$EDREQ
EDREQ = na.omit(EDREQ)
EDREQ = EDREQ[EDREQ != ""]

optionsEDREQ = surv %>%
  count(surv$EDREQ) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(EDREQ))

sum(optionsEDREQ$proportion)
optionsEDREQ


```


#### INFO
**Information on wildlife health can be acquired through continuing education rather than in undergraduate courses**
```{r}

INFO = surv$INFO
INFO = na.omit(INFO)
INFO = INFO[INFO != ""]

optionsINFO = surv %>%
  count(surv$INFO) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(INFO))

sum(optionsINFO$proportion)
optionsINFO


```


#### HANDSON
**All critical elements (including aspects of wildlife health) can be acquired through on-the-job training and experience**
```{r}

HANDSON = surv$HANDSON
HANDSON = na.omit(HANDSON)
HANDSON = HANDSON[HANDSON != ""]

optionsHANDSON = surv %>%
  count(surv$HANDSON) %>%
  rename(count = n) %>%
  mutate(proportion = count / length(HANDSON))

sum(optionsHANDSON$proportion)
optionsHANDSON


```
#TABLES 
```{r}

# library(purrr)
# 
# response_tables = list(
#       responsesumAGE = responsesumAGE,
#       responseSOURCE = responseSOURCE,
#       responseFREEINFO = responseFREEINFO,
#       responseTOPICS = responseTOPICS,
#    responseFIELD = responsesumFIELD,
#    responseCOUNTIES = responseCOUNTIES)
# 
# option_tables = list(
#   optionsCOUNTIES = optionsCOUNTIES,
#   optionssumCOUNTIES = optionssumCOUNTIES,
#   optionsGENDER = optionsGENDER,
#   optionsRACE = optionsRACE,
#   optionsETHNICITY = optionsETHNICITY,
#   optionsINCOME = optionsINCOME,
#   optionsAFFILIATE = optionsAFFILIATE,
#   optionsACTIVITY = optionsACTIVITY,
#   optionsSOURCE = optionsSOURCE,
#   optionssumSOURCE = optionssumSOURCE,
#   optionsACCESS = optionsACCESS,
#   optionsINTEREST = optionsINTEREST,
#   optionsFREEINFO = optionsFREEINFO,
#   optionssumFREEINFO = optionssumFREEINFO,
#   optionsTOPICS = optionsTOPICS,
#   optionssumTOPICS = optionssumTOPICS,
#   optionsEDUCATION = optionsEDUCATION,
#   optionsDEGREE = optionsDEGREE,
#   optionsCOURSE = optionsCOURSE,
#   optionsCOURSETIME = optionsCOURSETIME,
#   optionsBIOTIME = optionsBIOTIME,
#   optionsTWS = optionsTWS,
#   optionsSELFTITLE = optionsSELFTITLE,
#   optionsLICENSE = optionsLICENSE,
#   optionsCONTACT = optionsCONTACT,
#   optionsFIELD = optionsFIELD,
#   optionsCOLLECT = optionsCOLLECT,
#   optionsHANDLE = optionsHANDLE,
#   optionsSTATE = optionsSTATE,
#   optionsPPE = optionsPPE,
#   optionsPPETIME = optionsPPETIME,
#   optionsPIGS = optionsPIGS,
#   optionsCWD = optionsCWD,
#   optionsCOVID = optionsCOVID,
#   optionsCOVIDSPILL = optionsCOVIDSPILL,
#   optionsRABIES = optionsRABIES,
#   optionsBRUCE = optionsBRUCE,
#   optionsFLU = optionsFLU,
#   optionsFLUAL = optionsFLUAL,
#   optionsRABIESAL = optionsRABIESAL,
#   optionsTURKEY = optionsTURKEY,
#   optionsCWDAL = optionsCWDAL,
#   optionsBATS = optionsBATS,
#   optionsPPEREQ = optionsPPEREQ,
#   optionsEHD = optionsEHD,
#   optionsDARWIN = optionsDARWIN,
#   optionsPOPRED = optionsPOPRED,
#   optionsPOPPLAN = optionsPOPPLAN,
#   optionsSURVEY = optionsSURVEY,
#   optionsVACCINE = optionsVACCINE,
#   optionsPREVAL = optionsPREVAL,
#   optionsDIVERSE = optionsDIVERSE,
#   optionsCONSEQ = optionsCONSEQ,
#   optionsCLIMATE = optionsCLIMATE,
#   optionsEDREQ = optionsEDREQ,
#   optionsINFO = optionsINFO,
#   optionsHANDSON = optionsHANDSON)
# 
# save_tables_as_csv = function(tables, prefix) {
#   walk2(tables, names(tables), ~write.csv(.x, paste0(prefix, "_", .y, ".csv"), row.names = FALSE))
# }
# 
# save_tables_as_csv(response_tables, "response")
# save_tables_as_csv(option_tables, "option")


```

