---
title: "Descriptive Statistics & Visualization"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: litera
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Notes
additional data sources for AL (projected, same extent) - https://github.com/rytomey/geo4AL

https://jtr13.github.io/cc19/likert.html - Reporting Likert / Attitude Results


## Useful Links

https://bioinformatics.ccr.cancer.gov/docs/data-visualization-with-r/pdf/combined.pdf

# Initialization

#### Packages

```{r include=FALSE}
require(sf)
require(tidyverse)
require(skimr)      # For comprehensive summaries
require(janitor)    # For tabulations
require(gtsummary)  # For publication-ready tables
require(gt)
require(dplyr)
require(writexl)
require(openxlsx)
require(scales)
require(ggplot2)
require(lubridate)
require(plotly)
require(forcats)
require(tidycensus)
require(ggiraph)
require(tmaptools)
require(tidyverse)
require(patchwork)
require(scales)
require(sf)
```

#### Data Import

```{r, echo= TRUE}

# ---- Set Paths ----
base     <- normalizePath(file.path("..", ".."), mustWork = FALSE)
analyses <- file.path(base, "analyses")
inp <- file.path(analyses, "inputs")
oup = file.path(analyses, "outputs")

# ---- Load Raw Dataset ----
psurv <- read.csv(file.path(oup, "processedsurv.csv"))  
dict <- read.csv(file.path(oup, "datadictionary.csv"))
rsurv <- read.csv(file.path(inp, "progressover60.csv"))

```

# Summary Statistics

### Skim

1.  Numeric variables

    -   Mean and Standard Deviation (SD): central tendency and dispersion
    -   Min and Max: range of responses
    -   Median: central point, robust to outliers
    -   Histogram: text-based distribution overview

2.  Factor and Character Variables

    -   For categorical or Likert-style variables: Number of unique levels
    -   Most frequent value (mode)
    -   Frequency of most frequent value Missing values count

3.  Logical Variables

    -   Proportion of TRUE/FALSE
    -   Number of missing values

4.  Date/Time Variables

    -   Minimum and maximum dates: useful for survey timing or duration analysis

    ```{r}

    # Variables ----------------
    ovars <- colnames(rsurv)
    pvars <- colnames(psurv)
    derived <- setdiff(pvars, ovars)
    original <- intersect(pvars, ovars)

    # Original -----------------------------------------------------
    oskim <- psurv %>%
      select(any_of(original)) %>%
      skim()
    print(oskim)

    # Derived ----------------------------------------------------------
    dskim <- psurv %>%
      select(any_of(derived)) %>%
      skim()
    print(dskim)

    # Export ---------------------------------------------------------
    oskim_df <- as.data.frame(oskim)
    dskim_df <- as.data.frame(dskim)
    wb <- createWorkbook()
    addWorksheet(wb, "Original Variables")
    addWorksheet(wb, "Derived Variables")
    writeData(wb, sheet = "Original Variables", oskim_df)
    writeData(wb, sheet = "Derived Variables", dskim_df)
    saveWorkbook(wb, file.path(oup, "SKIMsummary.xlsx"), overwrite = TRUE)

    ```

### GT - Individual

```{r}

# Identifying varibles ----------------------------
glimpse(dict)
catVAR <- dict %>%
  filter(IsFactor) %>%
  pull(Variable)

# Function -----------------------
catTAB <- lapply(cat_vars, function(var) {
  tab <- tabyl(psurv[[var]])
  tab <- adorn_totals(tab)
  tab <- adorn_percentages(tab, "col") %>%
         adorn_pct_formatting()
  names(tab)[1] <- var
  return(tab)
})
names(catTAB) <- catVAR

# Export -------------------------------
wb <- createWorkbook()
for (var in names(catTAB)) {
  addWorksheet(wb, var)
  writeData(wb, var, catTAB[[var]])
}
saveWorkbook(wb, file.path(oup, "categoricTables.xlsx"), overwrite = TRUE)

```

### GT - By Section

```{r}

# Variables -----------------------------------------------------------
demo_vars <- c("RACE", "ETHNICITY", "GENDER", "INCOME", "EDUCATION", "RESIDENT", "DEGREE", "COURSE", "COURSETIME", "SELFTITLE", "AFFILIATE", "ACTIVITY", "BIOTIME")
know_vars <- c("PIGS", "BRUCE", "CWD", "FLUAL", "FLU", "COVID", "COVIDSPILL", "RABIESAL", "RABIES", "TURKEY")
conf_vars <- c("PIGS_K", "BRUCE_K", "CWD_K", "FLUAL_K", "FLU_K", "COVID_K", "COVIDSPILL_K", "RABIESAL_K", "RABIES_K", "TURKEY_K")
tude_vars <- c("POPRED", "POPPLAN", "SURVEY", "VACCINE", "PREVAL", "DIVERSE", "CONSEQ", "CLIMATE", "EDREQ", "INFO", "HANDSON", "CWDAL", "BATS", "PPEREQ", "EHD", "DARWIN", "ACCESS", "INTEREST")
prac_vars <- c("LICENSE", "CONTACT", "FIELD", "COLLECT", "HANDLE", "STATE", "PPE", "PPETIME")

# Function -----------------------
gtSUM <- function(data, vars, title) {
  data %>%
    select(any_of(vars)) %>%
    mutate(across(everything(), ~ if (is.character(.)) as.factor(.) else .)) %>%
    tbl_summary(
      by = NULL,
      statistic = list(all_categorical() ~ "{n} ({p}%)"),
      missing_text = "Missing",
      digits = all_categorical() ~ c(0, 1)) %>%
    modify_caption(title) %>%
    modify_header(label ~ "**Variable**", stat_0 ~ "**n (%)**") %>%
    bold_labels() %>%
    italicize_levels() %>%
    as_gt() %>%
    gt::tab_options(
      table.font.size = "small",
      data_row.padding = gt::px(2),
      table.align = "left")
}

# Generate gtsummary tables ------------------------------
gtTABd <- gtSUM(psurv, demo_vars, "**Demographic Summary**")
gtTABk <- gtSUM(psurv, know_vars, "**Knowledge Summary**")
gtTABc <- gtSUM(psurv, conf_vars, "**Confidence Summary**")
gtTABa <- gtSUM(psurv, tude_vars, "**Attitude Summary**")
gtTABp <- gtSUM(psurv, prac_vars, "**Practice Summary**")
gtTABd
gtTABk
gtTABc
gtTABa
gtTABp

# Export to Excel -----------------------------
wb <- createWorkbook()
tables <- list(
  Demographics = gtTABd,
  Knowledge = gtTABk,
  Confidence = gtTABc,
  Attitudes = gtTABa,
  Practices = gtTABp)
for (name in names(tables)) {
  df <- as.data.frame(tables[[name]]$table_body)
  addWorksheet(wb, name)
  writeData(wb, name, df)
}
saveWorkbook(wb, file.path(oup, "CategoricalTables.xlsx"), overwrite = TRUE)

```


# Specific

#### progress

```{r}
# Progress / 10% Intervals ------------------------------
prog <- read.csv(file.path(inp, "prog.csv")) # 215 responses - all progress made 
intFUN <- function(df, column = "PROG") {
  df %>%
    mutate(
      prog_bin = cut(
        .data[[column]],
        breaks = seq(0, 100, by = 10),
        include.lowest = TRUE,
        right = FALSE,
        labels = paste0(seq(0, 90, 10), "-", seq(10, 100, 10), "%"))) %>%
    count(prog_bin, name = "Respondent_Count") %>%
    arrange(prog_bin)
}
TPROG <- intFUN(prog)
TPROG
```

#### duration (min)

```{r}
# Duration Summary ---------------------------------------------
psurv <- psurv %>% mutate(DURATION = as.numeric(DURATION))
total_responses <- nrow(psurv)
above_60 <- sum(psurv$DURATION > 60)
summary(psurv$DURATION)
duration_table <- psurv %>%
  filter(DURATION <= 60) %>%
  mutate(duration_bin = cut(DURATION, breaks = seq(0, 60, by = 5), include.lowest = TRUE, right = FALSE,
                            labels = paste0(seq(0, 55, 5), "-", seq(5, 60, 5), " Minutes"))) %>%
  count(duration_bin, name = "Respondent_Count") %>%
  mutate(Proportion = Respondent_Count / total_responses)
duration_table_gt <- duration_table %>%
  gt() %>%
  tab_header(
    title = md("**Survey Completion Time (≤ 60 Minutes)**"),
    subtitle = md(glue::glue("Distribution of responses in 5-minute intervals ({total_responses} total; {above_60} >60 min excluded)"))) %>%
  cols_label(duration_bin = md("**Duration Interval**"), Respondent_Count = md("**Number of Respondents**"), Proportion = md("**Proportion of Total**")) %>%
  fmt_number(columns = vars(Respondent_Count), decimals = 0) %>%
  fmt_percent(columns = vars(Proportion), decimals = 1) %>%
  tab_options(table.font.size = "small", heading.title.font.size = 14, heading.subtitle.font.size = 12, data_row.padding = px(3), table.align = "left")
duration_table_gt

# End Date ------------------
psurv <- psurv %>% mutate(EDATE = as.Date(EDATE, format = "%m/%d/%Y"))
monthly_summary <- psurv %>%
  mutate(Month = format(EDATE, "%Y-%m")) %>%
  count(Month, name = "Respondent_Count") %>%
  mutate(Proportion = Respondent_Count / sum(Respondent_Count))
monthly_summary_gt <- monthly_summary %>%
  gt() %>%
  tab_header(
    title = md("**Survey Responses by Month**"),
    subtitle = md(glue::glue("Distribution of responses over time ({sum(monthly_summary$Respondent_Count)} total responses)"))) %>%
  cols_label(Month = md("**Month**"), Respondent_Count = md("**Number of Respondents**"), Proportion = md("**Proportion of Total**")) %>%
  fmt_number(columns = vars(Respondent_Count), decimals = 0) %>%
  fmt_percent(columns = vars(Proportion), decimals = 1) %>%
  tab_options(table.font.size = "small", heading.title.font.size = 14, heading.subtitle.font.size = 12, data_row.padding = px(3), table.align = "left")
monthly_summary_gt

```

### date ended

```{r}
# END DATE (SURVEY) -------------------------
# https://r-graph-gallery.com/163-interactive-area-chart-plotly.html
psurv <- psurv %>%
  mutate(EDATE = as.Date(EDATE, format = "%m/%d/%Y"))
daily_responses <- psurv %>%
  count(EDATE, name = "Respondent_Count") %>%
  arrange(EDATE)
timeP <- plot_ly(daily_responses,
               x = ~EDATE,
               y = ~Respondent_Count,
               type = 'scatter',
               mode = 'lines',
               fill = 'tozeroy',
               line = list(color = 'rgba(0,100,80,1)'),
               fillcolor = 'rgba(0,100,80,0.2)',
               hoverinfo = 'x+y',
               name = 'Responses') %>%
  layout(title = "Daily Survey Responses Over Time",
         xaxis = list(title = "Date"),
         yaxis = list(title = "Number of Responses"),
         hovermode = "x unified")
timeP
require(htmlwidgets)
saveWidget(timeP, file="timeP.html")
```

# Spatial
https://walker-data.com/census-r/index.html


### Setup

```{r}

# Set Census API Key
census_api_key("fc56686276a91cda05036e565b41bbb3a65010c8", install = TRUE, overwrite = TRUE)

clean_theme <- theme_minimal(base_family = "serif") +
  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
    axis.text = element_blank(), 
    axis.title = element_blank(), 
    axis.ticks = element_blank(),       
    panel.border = element_blank(),     
    plot.title = element_text(size = 16, face = "bold"),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10))

theme_map <- theme_void(base_family = "serif") +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10))
```

## ACS Data

| **Survey Variable** | **ACS Equivalent** | **ACS Table(s)** | **Description** |
|--------------|--------------|--------------|-------------------------------|
| `DOB` | Age distribution | B01001, B01002 | Age is reported in bands; B01001 provides detailed breakdowns, B01002 gives median age by county. |
| `RESIDENT`, `ZIPCODE` | Geographic identification | GEOID, NAME | GEOID and NAME provide standardized geographic identifiers at the county level; ZIP codes are not directly matched in ACS. |
| `RACE` | Race categories | B02001 | Detailed breakdowns of self-identified race categories. |
| `ETHNICITY` | Hispanic or Latino origin | B03003 | Captures ethnicity separate from race, as per Census classification. |
| `GENDER` | Sex | B01001 | Provides male and female population counts. |
| `INCOME` | Household income and poverty | B19013, B17001 | B19013 offers median household income; B17001 details poverty status by age and sex. |
| `EDUCATION` | Educational attainment | B15003 | Comprehensive breakdown of highest level of education completed. |
| `ATTITUDEbin` | Health insurance coverage | B27001 | Shows coverage status by age and sex, serving as a proxy for healthcare access. |

### Retrieve + Clean Tables

```{r}
# List of relevant ACS tables
acs_tables <- c("B01001", "B01002", "B02001", "B03003", "B19013", "B17001", "B15003", "B27001")

# Retrieve 2022 5-year ACS data for all counties in Alabama
acs_data <- lapply(acs_tables, function(table) {
  get_acs(geography = "county", state = "AL", table = table, year = 2022, survey = "acs1", geometry = FALSE)
})

# Assign names to the list elements
names(acs_data) <- acs_tables


# Clean and prepare each table -----------------------

sex_data <- acs_data[["B01001"]] %>%
  filter(variable %in% c("B01001_002", "B01001_026")) %>%
  mutate(sex = case_when(
    variable == "B01001_002" ~ "Male",
    variable == "B01001_026" ~ "Female"
  )) %>%
  select(GEOID, sex, estimate) %>%
  pivot_wider(names_from = sex, values_from = estimate) %>%
  mutate(total_sex_count = Male + Female)


# Age distribution
age_data <- acs_data[["B01001"]] %>%
  group_by(GEOID, NAME) %>%
  summarize(total_population = sum(estimate), .groups = "drop")

# Median age
median_age <- acs_data[["B01002"]] %>%
  select(GEOID, NAME, estimate) %>%
  rename(median_age = estimate)

# Race
race_data <- acs_data[["B02001"]] %>%
  select(GEOID, NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate)

# Ethnicity
ethnicity_data <- acs_data[["B03003"]] %>%
  select(GEOID, NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate)

# Median household income
income_data <- acs_data[["B19013"]] %>%
  select(GEOID, NAME, estimate) %>%
  rename(median_household_income = estimate)

# Poverty status
poverty_data <- acs_data[["B17001"]] %>%
  filter(variable == "B17001_002") %>%
  select(GEOID, NAME, estimate) %>%
  rename(pop_below_poverty = estimate)

# Education
education_data <- acs_data[["B15003"]] %>%
  filter(variable %in% c("B15003_022", "B15003_023", "B15003_024", "B15003_025")) %>%
  group_by(GEOID, NAME) %>%
  summarize(edu_bachelor_plus = sum(estimate), .groups = "drop")
# Education: Bachelor's degree or higher
# B15003_022: Bachelor's degree
# B15003_023: Master's degree
# B15003_024: Professional school degree
# B15003_025: Doctorate degree

# Health insurance
insurance_data <- acs_data[["B27001"]] %>%
  filter(variable == "B27001_001") %>%
  select(GEOID, NAME, estimate) %>%
  rename(total_insured = estimate)

```

### Merge + Export

```{r}

acs_combined <- age_data %>%
  left_join(median_age, by = c("GEOID", "NAME")) %>%
  left_join(race_data, by = c("GEOID", "NAME")) %>%
  left_join(ethnicity_data, by = c("GEOID", "NAME")) %>%
  left_join(income_data, by = c("GEOID", "NAME")) %>%
  left_join(poverty_data, by = c("GEOID", "NAME")) %>%
  left_join(education_data, by = c("GEOID", "NAME")) %>%
  left_join(insurance_data, by = c("GEOID", "NAME")) %>%
  left_join(sex_data, by = c("GEOID"))


gsurv <- read.csv(file.path(oup, "processedsurv.csv"))  
county <- st_read('/vsicurl/https://github.com/rytomey/geo4al/raw/main/boundaries/alabama/countyAlabama.shp')

gsurv <- gsurv %>%
  mutate(LOCATION = str_to_upper(str_trim(LOCATION)) %>%
           str_remove_all(" COUNTY$"))
acs_combined <- acs_combined %>%
  mutate(LOCATION = str_to_upper(NAME) %>%
           str_remove_all(", ALABAMA") %>%
           str_remove_all(" COUNTY$")) # %>% 
       #    str_trim()) %>%
      #  group_by(LOCATION) %>%
  #  summarize(across(everything(), first), .groups = "drop")
county_clean <- county %>%
  mutate(LOCATION = str_to_upper(str_trim(NAMELSAD)) %>%
           str_remove_all(" COUNTY$"))

gsurv$LOCATION
acs_combined$LOCATION
county_clean$LOCATION

acs_geo <- county_clean %>%
  st_join(acs_geo, by = "LOCATION")
st_write(acs_geo, file.path(oup, "acs_combined.gpkg"), delete_layer = TRUE) 

acs_combined <- acs_combined %>%
  mutate(LOCATION = str_to_upper(NAME) %>%
           str_remove_all(", ALABAMA") %>%
           str_remove_all(" COUNTY$")  %>% 
           str_trim()) %>%
       group_by(LOCATION) %>%
    summarize(across(everything(), first), .groups = "drop")
acs_geo <- acs_combined %>%
  left_join(county_clean, "geometry", by = "LOCATION")
gsurv <- acs_geo %>%
  left_join(gsurv, by = "LOCATION")
gsurv
st_write(gsurv, file.path(oup, "psurv_geo_data.gpkg"), delete_layer = TRUE)

```

### E.g. of potential uses

```{r}
# Bubble Chart --------------
ggplot(gsurv, aes(x = median_age, 
                         y = median_household_income, 
                         size = pop_below_poverty, 
                         label = LOCATION)) +
  geom_point(alpha = 0.6, color = "steelblue") +
  scale_size_continuous(range = c(2, 12), name = "Population Below Poverty") +
  scale_y_continuous(labels = label_dollar()) +
  labs(
    title = "County Demographics: Age, Income & Poverty",
    subtitle = "2022 ACS 1-Year Estimates, Alabama Counties",
    x = "Median Age",
    y = "Median Household Income",
    caption = "Source: U.S. Census Bureau, ACS 1-Year Estimates"
  ) +
  theme_minimal(base_family = "serif") +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10))

# Map ------------------------------------------------
# Count respondents by county
respondents_count <- gsurv %>%
  count(LOCATION, name = "RESPONDENTS")

# Merge with county geometry data
map_data <- county_clean %>%
  left_join(respondents_count, by = "LOCATION") %>%
  mutate(RESPONDENTS = factor(RESPONDENTS))

# Plot map
countyn = ggplot(map_data) +
  geom_sf(aes(fill = RESPONDENTS), color = "white") +
  scale_fill_viridis_d(
    option = "plasma",
    na.value = "grey",
    name = "Count") +
  labs(title = "Survey Respondents by County") +
  clean_theme
countyn

```
# National election mapping with tigris shapes
```{r}

# Data source: https://cookpolitical.com/2020-national-popular-vote-tracker
vote2020 <- read_csv("data/us_vote_2020.csv")
us_states <- states(cb = TRUE, resolution = "20m") %>%
  filter(NAME != "Alabama") %>%
  shift_geometry()

```
