---
title: "Spatial Visualization and Exploration"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document:
    toc: true
    number_sections: true
    fig_caption: true
  pdf_document:
    toc: true
    number_sections: true
    fig_caption: true
    highlight: zenburn
    latex_engine: xelatex
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    theme: readable
    highlight: tango
    code_folding: show
    fig_caption: true
    df_print: paged
editor_options:
  chunk_output_type: inline
fontsize: 10pt
mainfont: "Times New Roman"
geometry: margin=1in
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
require(tidyverse)
require(zipcodeR)
require(ggmap)
require(sf)
require(knitr)
require(dplyr)
require(tigris)
options(tigris_use_cache = TRUE)
require(ggplot2)
require(RColorBrewer)
```

**Ideas:**
**-county of wildlife biologists/ handling vs county population/income vs respondent** 
**county of respondents | Knowledge Individual/overall | Topics interested | Practices | CDC county prevalence/presence* 
**county of wildlife biologists residence (note: not exactly where they work)**
**county of wildlife handling in Alabama (this is the bigger one for me)**
**county of where biologists handle wildlife ~ education (tiered heat map or something**
**COUNTIES versus respondent distribution/count**

### Importing Data 
```{r include=FALSE}

# ---- Set Paths ----
base     <- normalizePath(file.path("..", ".."), mustWork = FALSE)
analyses <- file.path(base, "analyses")
inp <- file.path(analyses, "inputs")
oup <- file.path(analyses, "outputs")

# ---- Load Raw Dataset ----
df <- read_csv(file.path(oup, "recodeddata.csv"))
nrow(df) # 140 responses ------
names(df)

```

# Converting ZIP
```{r}

df <- df %>%
  mutate(ZIPCODE = as.character(ZIPCODE)) %>%
  left_join(
    zipcodeR::zip_code_db %>%
      dplyr::select(zipcode, county, state),
    by = c("ZIPCODE" = "zipcode")) %>%
  rename(COUNTY = county) %>%
  dplyr::select(-state)

# Map of Respondents / County ----------------
alcounty <- counties(state = "AL", cb = TRUE, class = "sf") %>%
  mutate(NAME = toupper(NAME))  
dfcounty <- df %>%
  filter(!is.na(COUNTY)) %>%
  count(COUNTY, name = "Respondents")
mapcounty <- alcounty %>%
  left_join(dfcounty, by = c("NAMELSAD" = "COUNTY")) %>%
  mutate(Respondents = replace_na(Respondents, 0))
centroids <- st_centroid(mapcounty)
centroids_coords <- centroids %>%
  mutate(
    lon = st_coordinates(geometry)[, 1],
    lat = st_coordinates(geometry)[, 2])

# MAP: Respondents / County ----------------------------------
ggcounty <- ggplot(mapcounty) +
  geom_sf(aes(fill = Respondents), color = "black", size = 1) +
 geom_text(
    data = centroids_coords,
    aes(x = lon, y = lat, label = ifelse(Respondents > 0, Respondents, "")),
    size = 3, color = "grey40") +
  scale_fill_distiller(
    palette = "YlGnBu",  # switch to 'greys' for B/W 
    direction = 1,
    name = "Respondents",
    breaks = range(mapcounty$Respondents, na.rm = TRUE),
    labels = round(range(mapcounty$Respondents, na.rm = TRUE))) +
  theme_minimal(base_size = 14) +
  labs(title = "Survey Respondents by County") +
  theme(
    legend.position = "right",
    legend.title = element_text(size = 10),
    legend.title.position = "top",
    legend.text = element_text(size = 10),
    panel.grid.major = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    plot.title = element_text(face = "bold"))
ggcounty

# Export ------
ggsave(filename = "county_respondents.pdf",plot = ggcounty, path = oup, width = 8, 
       height = 6,units = "in") # Vector PDF
ggsave(filename = "county_respondents.tif",plot = ggcounty, path = oup, width = 8, 
       height = 6,dpi = 600, units = "in") # TIFF
```

# Census Data Import
| **Survey Variable** | **ACS Equivalent** | **ACS Table(s)** | **Description** |
|--------------|--------------|--------------|-------------------------------|
| `DOB` | Age distribution | B01001, B01002 | Age is reported in bands; B01001 provides detailed breakdowns, B01002 gives median age by county. |
| `RESIDENT`, `ZIPCODE` | Geographic identification | GEOID, NAME | GEOID and NAME provide standardized geographic identifiers at the county level; ZIP codes are not directly matched in ACS. |
| `RACE` | Race categories | B02001 | Detailed breakdowns of self-identified race categories. |
| `ETHNICITY` | Hispanic or Latino origin | B03003 | Captures ethnicity separate from race, as per Census classification. |
| `GENDER` | Sex | B01001 | Provides male and female population counts. |
| `INCOME` | Household income and poverty | B19013, B17001 | B19013 offers median household income; B17001 details poverty status by age and sex. |
| `EDUCATION` | Educational attainment | B15003 | Comprehensive breakdown of highest level of education completed. |
| `ATTITUDEbin` | Health insurance coverage | B27001 | Shows coverage status by age and sex, serving as a proxy for healthcare access. |
```{r}
require(tidycensus)
#-----------------------------------------------------------------------------
#--Copied this code from a different script-----------------------------------
#--Will likely need some cleaning to work---------------------------------------
#-----------------------------------------------------------------------------

# Set Census API Key
census_api_key("fc56686276a91cda05036e565b41bbb3a65010c8", install = TRUE, overwrite = TRUE)

# List of relevant ACS tables
acs_tables <- c("B01001", "B01002", "B02001", "B03003", "B19013", "B17001", "B15003", "B27001")

# Retrieve 2022 5-year ACS data for all counties in Alabama
acs_data <- lapply(acs_tables, function(table) {
  get_acs(geography = "county", state = "AL", table = table, year = 2022, survey = "acs1", geometry = FALSE)
})

# Assign names to the list elements
names(acs_data) <- acs_tables


# Clean and prepare each table -----------------------

sex_data <- acs_data[["B01001"]] %>%
  filter(variable %in% c("B01001_002", "B01001_026")) %>%
  mutate(sex = case_when(
    variable == "B01001_002" ~ "Male",
    variable == "B01001_026" ~ "Female"
  )) %>%
  select(GEOID, sex, estimate) %>%
  pivot_wider(names_from = sex, values_from = estimate) %>%
  mutate(total_sex_count = Male + Female)


# Age distribution
age_data <- acs_data[["B01001"]] %>%
  group_by(GEOID, NAME) %>%
  summarize(total_population = sum(estimate), .groups = "drop")

# Median age
median_age <- acs_data[["B01002"]] %>%
  select(GEOID, NAME, estimate) %>%
  rename(median_age = estimate)

# Race
race_data <- acs_data[["B02001"]] %>%
  select(GEOID, NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate)

# Ethnicity
ethnicity_data <- acs_data[["B03003"]] %>%
  select(GEOID, NAME, variable, estimate) %>%
  pivot_wider(names_from = variable, values_from = estimate)

# Median household income
income_data <- acs_data[["B19013"]] %>%
  select(GEOID, NAME, estimate) %>%
  rename(median_household_income = estimate)

# Poverty status
poverty_data <- acs_data[["B17001"]] %>%
  filter(variable == "B17001_002") %>%
  select(GEOID, NAME, estimate) %>%
  rename(pop_below_poverty = estimate)

# Education
education_data <- acs_data[["B15003"]] %>%
  filter(variable %in% c("B15003_022", "B15003_023", "B15003_024", "B15003_025")) %>%
  group_by(GEOID, NAME) %>%
  summarize(edu_bachelor_plus = sum(estimate), .groups = "drop")
# Education: Bachelor's degree or higher
# B15003_022: Bachelor's degree
# B15003_023: Master's degree
# B15003_024: Professional school degree
# B15003_025: Doctorate degree

# Health insurance
insurance_data <- acs_data[["B27001"]] %>%
  filter(variable == "B27001_001") %>%
  select(GEOID, NAME, estimate) %>%
  rename(total_insured = estimate)

acs_combined <- age_data %>%
  left_join(median_age, by = c("GEOID", "NAME")) %>%
  left_join(race_data, by = c("GEOID", "NAME")) %>%
  left_join(ethnicity_data, by = c("GEOID", "NAME")) %>%
  left_join(income_data, by = c("GEOID", "NAME")) %>%
  left_join(poverty_data, by = c("GEOID", "NAME")) %>%
  left_join(education_data, by = c("GEOID", "NAME")) %>%
  left_join(insurance_data, by = c("GEOID", "NAME")) %>%
  left_join(sex_data, by = c("GEOID"))


gsurv <- read.csv(file.path(oup, "processedsurv.csv"))  
county <- st_read('/vsicurl/https://github.com/rytomey/geo4al/raw/main/boundaries/alabama/countyAlabama.shp')

gsurv <- gsurv %>%
  mutate(LOCATION = str_to_upper(str_trim(LOCATION)) %>%
           str_remove_all(" COUNTY$"))
acs_combined <- acs_combined %>%
  mutate(LOCATION = str_to_upper(NAME) %>%
           str_remove_all(", ALABAMA") %>%
           str_remove_all(" COUNTY$")) # %>% 
       #    str_trim()) %>%
      #  group_by(LOCATION) %>%
  #  summarize(across(everything(), first), .groups = "drop")
county_clean <- county %>%
  mutate(LOCATION = str_to_upper(str_trim(NAMELSAD)) %>%
           str_remove_all(" COUNTY$"))

gsurv$LOCATION
acs_combined$LOCATION
county_clean$LOCATION

acs_geo <- county_clean %>%
  st_join(acs_geo, by = "LOCATION")
st_write(acs_geo, file.path(oup, "acs_combined.gpkg"), delete_layer = TRUE) 

acs_combined <- acs_combined %>%
  mutate(LOCATION = str_to_upper(NAME) %>%
           str_remove_all(", ALABAMA") %>%
           str_remove_all(" COUNTY$")  %>% 
           str_trim()) %>%
       group_by(LOCATION) %>%
    summarize(across(everything(), first), .groups = "drop")
acs_geo <- acs_combined %>%
  left_join(county_clean, "geometry", by = "LOCATION")
gsurv <- acs_geo %>%
  left_join(gsurv, by = "LOCATION")
gsurv
st_write(gsurv, file.path(oup, "psurv_geo_data.gpkg"), delete_layer = TRUE)

```

# Disease Data 
**Links to data aquisition sources**
https://www.cdc.gov/lyme/data-research/facts-stats/lyme-disease-case-map.html?CDC
https://www.cdc.gov/bird-flu/situation-summary/data-map-wild-birds.html
https://www.cdc.gov/bird-flu/situation-summary/data-map-commercial.html
https://www.sciencebase.gov/catalog/item/58068050e4b0824b2d1d415d
```{r}

cwdC <- read_csv(file.path(inp, "cwdCaptive 2024.csv"))
cwdW <- read_csv(file.path(inp, "cwdWild2024.csv"))
fluP <- read_csv(file.path(inp, "h5n1poultry2025.csv"))
fluW <- read_csv(file.path(inp, 
                           "h5n1wildbirds2025.csv"))
lyme <- read_csv(file.path(inp, "lyme2023.csv"))

```


